---
editor_options:
  markdown:
    wrap: 72
output:
  html_document:
    df_print: paged
---

# TurboID figures

Henry Sanford
[hsanford\@rockefeller.edu](mailto:hsanford@rockefeller.edu){.email}

```{r}
source("utils_turboid.R")


dep_path <- paste0(PIPELINE_RESULTS_PATH, "turboid_differential_expression.csv")

go_path <- paste0(PIPELINE_RESULTS_PATH, "turboid_go_term_analysis.csv")


replace_list <- c(
  "Intracellular" = "Intracellular",
  "Signal_Peptide" = "Signal Peptide",
  "Transmembrane" = "Transmembrane",
  "UPS" = "UPS",
  "NA" = "Other"
)
palette <- c(
  "Signal Peptide" = "#721f81",
  "Intracellular" = "#b73779",
  "UPS" = "#f1605d",
  "Transmembrane" = "#feb078",
  "Other" = "lightgrey"
)
```

# Figure 1


## 1H: Abundance plots

Pull tissue enriched and tissue enhanced genes from human protein atlas

-   Cell type enriched: At least four-fold higher mRNA level in a
    particular tissue/cell type compared to any other tissues/cell
    types.
-   Group enriched: At least four-fold higher average mRNA level in a
    group of 2-5 tissues or 2-10 cell types compared to any other
    tissues/cell types.
-   Cell type enhanced: At least four-fold higher mRNA level in a
    particular tissue/cell type compared to the average level in all
    other tissues/cell types.

```{r, fig.width=8, fig.height=2.3}
hpa_data_three_tissues <- NULL
tissues_to_download <- c("Adipocytes" = "adip", "Hepatocytes" = "alb", "B-cells" = "CD19")
for (tissue in names(tissues_to_download)) {
  for (category in c("Cell+type+enhanced", "Cell+type+enriched", "Group+enriched")) {
    url <- paste0(
      "https://www.proteinatlas.org/search/cell_type_category_rna%3A",
      tissue,
      "%3B",
      category,
      "+AND+sort_by%3Atissue+specific+score?format=tsv"
    )
    hpa_data_three_tissues <- GET(url) %>%
      content(as = "text") %>%
      read_delim(show_col_types = FALSE) %>%
      mutate(
        tissue = tissues_to_download[tissue],
        hpa_category = gsub("\\+", " ", category)
      ) %>%
      rbind(hpa_data_three_tissues)

    Sys.sleep(0.1)
  }
}

hpa_data <- hpa_data_three_tissues %>%
  mutate(synonyms = paste0(Gene, ", ", `Gene synonym`)) %>%
  separate_rows(synonyms, sep = ", ") %>%
  filter(synonyms != "NA") %>%
  mutate(key = paste(synonyms, tissue)) %>%
  dplyr::select(synonyms, tissue, key, hpa_category, `RNA single cell type specificity`, `RNA single cell type specific nCPM`)

### Make abundance plot

proteins_to_highlight <- c("TLR9_CD19", "MZB1_CD19", "IGJ_CD19", "IGHM_CD19", "CR2_CD19", "ITGAL_CD19", "ITGB2_CD19", "TRFE_alb", "MBL2_alb", "KNG1_alb", "ITIH1_alb", "HPT_alb", "HEMO_alb", "C3_alb", "APOH_alb", "APOB_alb", "RETN_adip", "PLIN4_adip", "PLIN1_adip", "NEGR1_adip", "LRG1_adip", "LPL_adip", "FABP4_adip", "DERM_adip", "APOE_adip", "ADIPO_adip", "PLIN4_adip", "FABP4_adip", "SPRC_adip", "GSYN_adip", "SPRC_adip", "LPL_adip", "CPN2_adip", "CD74_CD19", "COFA1_adip", "MA2B1_CD19", "LIFR_adip", "IRAG2_CD19", "IRF8_CD19", "MOT8_alb", "TINAL_adip")

tissue_abundance_data <-
  read_experiment("20220818_EV1_105", "tissue") %>%
  add_alias() %>%
  # calculate mean signal intensity
  dplyr::select(c(alias, uniprot_id, Symbol_human_jackson_homology_db, `SWISS_PROT IDs_human_jackson_homology_db`) | contains("cre+")) %>%
  dplyr::select(-contains("cre-")) %>%
  pivot_longer(cols = -c(uniprot_id, alias, Symbol_human_jackson_homology_db, `SWISS_PROT IDs_human_jackson_homology_db`)) %>%
  mutate(tissue = str_split(name, "_") %>% map_chr(1)) %>%
  group_by(uniprot_id, alias, tissue, Symbol_human_jackson_homology_db, `SWISS_PROT IDs_human_jackson_homology_db`) %>%
  summarise(log2_mean_SI = log2(mean(value))) %>%
  group_by(tissue) %>%
  # add metadata for plotting
  mutate(
    # add signal intensity rank
    rank = order(order(log2_mean_SI, decreasing = TRUE)),
    # add tissue name for plotting
    tissue_name = recode(
      tissue,
      "alb" = "Albumin-Cre liver",
      "adip" = "Adiponectin-Cre iWAT",
      "CD19" = "CD19-Cre spleen"
    ),
    # convert tissue name to factor for plot order
    tissue_name = factor(
      tissue_name,
      levels = c("Albumin-Cre liver", "Adiponectin-Cre iWAT", "CD19-Cre spleen")
    ),
    human_gn = str_split(`Symbol_human_jackson_homology_db`, ",") %>% map_chr(1),
    key = paste(human_gn, tissue),
    highlight = tolower(key) %in% tolower(hpa_data$key),
    label = (paste0(alias, "_", tissue) %in% proteins_to_highlight) & (highlight),
    label_name = case_when(label ~ alias, TRUE ~ "")
  )

tissue_abundance_data %>%
  arrange(label, highlight) %>%
  ggplot(aes(x = rank, y = log2_mean_SI, label = label_name, fill = highlight, stroke = label, alpha = label)) +
  geom_point(
    shape = 21,
    show.legend = FALSE
  ) +
  geom_text_repel(
    size = 2.11667,
    family = FONT_FAMILY,
    segment.size = LINE_WIDTH,
    min.segment.length = 0,
    max.overlaps = Inf,
    show.legend = FALSE
  ) +
  facet_wrap(~tissue_name, scales = "free") +
  labs(
    x = "protein rank",
    y = expression("log"[2] * "(mean signal intensity)")
  ) +
  turboid_theme() +
  theme(aspect.ratio = 1, strip.text.x.top = element_text(family = FONT_FAMILY, size = 8, color = "black"), panel.spacing.x = unit(0.4, "cm")) +
  scale_fill_manual(
    values = c(
      "TRUE" = POINT_FILL,
      "FALSE" = "grey90"
    )
  ) +
  scale_discrete_manual(aesthetics = "stroke", values = c("TRUE" = LINE_WIDTH, "FALSE" = 0)) +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.5))

hpa_data %>%
  write_csv(paste0(PIPELINE_RESULTS_PATH, "hpa_data_three_tissues.csv"))

save_plot("1h_abundance_plot", wd = 8, ht = 2.5)
```

## S1G: Percent barplot

```{r, fig.height=1.1, fig.width=2.2}
percent_barplot_theme <- function(ggplot_obj) {
  # theme to be applied to stacked barplots throughout
  # manuscript
  ggplot_obj +
    scale_x_continuous(
      labels = scales::percent_format(accuracy = 1, suffix = ""),
      breaks = c(0, 0.5, 1),
      expand = expansion(mult = c(0, 0))
    ) +
    guides(fill = guide_legend(reverse = TRUE)) +
    labs(fill = NULL) +
    # percent axis labels
    labs(x = NULL, y = NULL) +
    ggtitle("% of proteins") +
    turboid_theme() +
    # no border line
    theme(
      panel.border = element_blank(),
      axis.line.x = AXIS_LINE,
      axis.line.y = AXIS_LINE,
    ) +
    theme(
      legend.key.size = unit(2, "mm"),
      legend.key.spacing.y = unit(0.75, "mm"),
      legend.position = "right",
      legend.justification = "center",
      legend.margin = margin(0, 0, 0, -5),
      plot.title = element_text(
        family = FONT_FAMILY,
        color = "black",
        size = FONT_SIZE,
        margin = margin(0, 0, 1, 0)
      ),
      legend.text = element_text(
        family = FONT_FAMILY,
        size = FONT_SIZE,
        color = "black",
        margin = margin(l = 1)
      )
    )
}
df <-
  "/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Mass-spectrometry-datasets/03_results/04_turboid_downstream_results/05_results/01_tissue/20220818_EV1_105/01_cutoff_ROC_filter/decision_table_20220818_EV1_105.xlsx" %>%
  readxl::read_excel() %>%
  rename(pass_cutoff_variable = "pass_cutoff_result") %>%
  dplyr::select(pass_cutoff_variable, "annotation")

# generate labels that include protein counts
not_pass_label <-
  paste0("not pass cutoff\n(", nrow(df %>% filter(pass_cutoff_variable == 0)), " proteins)")
pass_label <-
  paste0("pass cutoff\n(", nrow(df %>% filter(pass_cutoff_variable == 1)), " proteins)")
all_label <- paste0("all\n(", nrow(df), " proteins)")

all_proteins <- df %>% mutate(pass_cutoff = all_label)

replace_list <-
  c("TP" = "True positive", "FP" = "False positive", "NA" = "Not annotated")
palette <- c(
  "Not annotated" = "#9B75A4",
  "False positive" = "#999CC1",
  "True positive" = "#8DB8C3"
)
obj <- df %>%
  mutate(pass_cutoff = case_when(
    pass_cutoff_variable == 1 ~ pass_label,
    TRUE ~ not_pass_label
  )) %>%
  rbind(all_proteins) %>%
  mutate(
    annotation = replace_na(annotation, replace = "NA"),
    annotation = recode(annotation, !!!replace_list),
    pass_cutoff = factor(pass_cutoff, levels = c(not_pass_label, pass_label, all_label)),
    annotation = factor(annotation, levels = names(palette))
  ) %>%
  ggplot(mapping = aes(y = pass_cutoff, fill = annotation)) +
  geom_bar(
    position = "fill",
    color = "black",
    size = LINE_WIDTH,
    width = 0.65
  ) +
  scale_fill_manual(values = palette)

percent_barplot_theme(obj)

save_plot("s1g_percent_barplot", wd = 2.2, ht = 1.1)
```

## S1H: PCA


```{r, fig.width=2, fig.height=3}
pca_palette <- c(
  "CD19-Cre+" = "#B5D336",
  "Albumin-Cre+" = "#26838F",
  "Adipo-Cre+" = "#AEB4DB"
)
"/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Data visualization/01_source_data/tissue/pca/20220818_EV1_105_normalized_pca.csv" %>%
  read_csv(show_col_types = FALSE) -> pca_df
# remap condition values
map <-
  setNames(
    c("Adipo-Cre+", "Albumin-Cre+", "CD19-Cre+"),
    c("alb_cre+", "adip_cre+", "CD19_cre+")
  )
pca_df$condition <- map[unlist(pca_df$condition)]
expansion <- 0.25
pca_df %>%
  mutate(condition = factor(condition, levels = names(pca_palette))) %>%
  ggplot(aes(
    x = `principal component 1`, y = `principal component 2`, fill =
      condition
  )) +
  geom_point(
    size = 2.5,
    shape = 21,
    alpha = 0.9,
    col = "black",
    stroke = LINE_WIDTH,
    show.legend = TRUE
  ) +
  turboid_theme() +
  labs(x = "PC1 (56.83%)", y = "PC2 (33.88%)") +
  legend_theme() +
  scale_fill_manual(
    values = pca_palette,
    name = NULL
  ) +
  scale_x_continuous(expand = expansion(mult = c(expansion, expansion))) +
  scale_y_continuous(expand = expansion(mult = c(expansion, expansion)))

save_plot("s1h_pca", wd = 2 + 0.05, ht = 3)
```

## 1G: GO-term enrichment

```{r, fig.height = 2.2, fig.width=3.3}
go_term_plot <-
  function(fn,
           domains,
           title,
           legend_position,
           height,
           width,
           string_wrap) {
    df <- fn %>%
      read_csv(show_col_types = FALSE) %>%
      filter(class %in% domains)
    df$class <- recode(
      df$class,
      "cellular_component" = "Cellular component",
      "biological_process" = "Biological process",
      "molecular_function" = "Molecular function"
    )
    print(df)
    df %>%
      arrange(p_fdr_bh) %>%
      head(10) %>%
      ggplot(aes(
        x = -log10(p_fdr_bh),
        y = reorder(str_wrap(term, width = string_wrap), -p_fdr_bh),
        size = n_genes,
      )) +
      geom_point(
        shape = 21,
        fill = POINT_FILL,
        stroke = LINE_WIDTH,
        color = "black"
      ) +
      geom_vline(
        xintercept = -log10(0.05),
        linetype = "dashed",
        colour = "grey",
        size = LINE_WIDTH
      ) +
      facet_wrap(~class, scales = "free") +
      labs(
        y = NULL,
        x = expression("-log"[10] * "(FDR)"),
        size = "proteins"
      ) +
      scale_x_continuous(expand = c(0.2, 0.2)) +
      ggtitle(title) +
      theme(legend.position = legend_position, legend.key.spacing.y = unit(1, "mm")) +
      turboid_theme() +
      scale_size_continuous(range = c(0.5, 3.5)) -> plot
    print(plot)
  }
go_term_plot(
  fn = "/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Mass-spectrometry-datasets/03_results/04_turboid_downstream_results/05_results/01_tissue/20220807_EV1_101/goterm_analysis/full_mouse_genome_background/goterm_full_mouse_genome_basal_cre+vs.cre-_up_go_term_results.csv",
  domains = c("cellular_component"),
  title = "Cre+ vs Cre-",
  legend_position = "right",
  height = 2.3,
  width = 3.5,
  string_wrap = 100
)

save_plot(
  "1g_go_term",
  ht = 2.2,
  wd = 3.3
)
```

## S1I-J: Signal P volcano plot

```{r, fig.width=2, fig.height=4}
volcano_plot_base <-
  function(df,
           params,
           left_annotation,
           right_annotation) {
    annotations <- data.frame(
      xpos = c(-Inf, Inf),
      ypos = c(Inf, Inf),
      annotateText = c(left_annotation, right_annotation),
      hjustvar = c(-0.1, 1.1)
    )
    df %>%
      arrange(group) %>%
      ggplot(aes(x = log2FC, y = `-log10_pval`, fill = group, alpha = group)) +
      geom_point(
        shape = 21,
        stroke = params$stroke,
        size = 1.2,
        show.legend = params$show_legend
      ) +
      legend_theme() +
      # make x axis a bit wider
      # scale_x_continuous(expand = expansion(mult = c(.05, .05))) +
      scale_fill_manual(values = params$palette) +
      scale_alpha_manual(values = params$alpha_palette, guide = "none") +
      labs(
        y = expression("-log"[10] * "(p-value)"),
        fill = NULL
      ) +
      geom_hline(
        yintercept = -log10(0.05),
        linetype = "dashed",
        size = LINE_WIDTH
      ) +
      geom_vline(
        xintercept = c(-LFC_CUTOFF, LFC_CUTOFF),
        linetype = "dashed",
        size = LINE_WIDTH
      ) +
      geom_text(
        data = annotations,
        aes(
          x = xpos,
          y = ypos,
          # hjust = hjustvar,
          label = annotateText,
        ),
        vjust = 1.25,
        hjust = "inward",
        nudge_x = 4,
        inherit.aes = FALSE,
        show.legend = FALSE,
        size = FONT_SIZE_MM,
        fontface = "italic",
        lineheight = 0.95
      )
  }

cre_volcano_plot <- function(df, cre_palette) {
  # pull top n proteins to label
  df %>%
    filter(group != "Other") %>%
    arrange(`-log10_pval`) %>%
    tail(10) -> lbl_df

  df %>%
    volcano_plot_base(
      params = list(palette = cre_palette, stroke = 0, show_legend = TRUE, alpha_palette = setNames(rep(0.6, length(signal_p_palette)), names(cre_palette))),
      left_annotation = " Elevated in\n Cre-",
      right_annotation = "Elevated in \nCre+ "
    ) +
    annotate(
      geom = "rect",
      xmin = log2(1.5),
      xmax = Inf,
      ymin = -log10(0.05),
      ymax = Inf,
      fill = "#FDE725FF",
      alpha = 0.5,
    ) +
    labs(x = expression("log"[2] * "(Adipo-Cre+/Adipo-Cre-)"))
}

read_experiment("20220818_EV1_105", "tissue") %>%
  rename(c(
    log2FC = "log2_FC_processed_census-out_20220818_EV1_105 - adip_cre+vs.cre- (2247 Proteins)",
    `-log10_pval` = "-log10_pval_processed_census-out_20220818_EV1_105 - adip_cre+vs.cre- (2247 Proteins)",
    `gene` = "gene_name"
  )) %>%
  dplyr::select(
    `Entry Name`,
    gene,
    log2FC,
    `-log10_pval`,
    `Signal peptide`,
    `Gene Ontology (cellular component)`
  ) %>%
  add_alias() -> df

# signal peptide volcano plot
signal_p_palette <-
  c(
    "Other" = "grey",
    "Signal peptide" = "cornflowerblue"
  )
df %>%
  mutate(
    group = case_when(is.na(`Signal peptide`) ~ "Other", TRUE ~ "Signal peptide"),
    group = factor(group, levels = names(signal_p_palette))
  ) %>%
  cre_volcano_plot(cre_palette = signal_p_palette)

save_plot("s1i_er_volcano", ht = 4, wd = 2)

# er protein volcano plot
er_palette <-
  c(
    "Other" = "grey",
    "Endoplasmic reticulum" = "hotpink4"
  )
df %>%
  mutate(
    group = case_when(
      str_detect(`Gene Ontology (cellular component)`, "GO:0005783") ~ "Endoplasmic reticulum",
      TRUE ~ "Other"
    ),
    group = factor(group, levels = names(er_palette))
  ) %>%
  cre_volcano_plot(cre_palette = er_palette)

save_plot("s1j_er_volcano", ht = 4, wd = 2)
```

## S2J summary barplot

```{r, fig.width=2.4, fig.height=2}
df <- dep_path %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    experiment == "20220818_EV1_105",
    grepl("cre", comparison) & !grepl("conditions", comparison),
    Regulation == "Significant Up"
  )


sp_df <- df %>%
  mutate(
    column = "Signal peptide",
    group = case_when(
      Outcyte == "Signal_Peptide" ~ "Signal peptide",
      TRUE ~ "Other"
    )
  )

er_df <- df %>%
  mutate(
    column = "Endoplasmic reticulum",
    group = case_when(
      str_detect(`Gene Ontology (GO)`, "GO:0005783") ~ "Endoplasmic reticulum",
      TRUE ~ "Other"
    ),
  )

obj <- rbind(
  sp_df,
  er_df
) %>%
  mutate(
    comparison = case_when(
      grepl("adip", comparison) ~ "Adipo-Cre",
      grepl("alb", comparison) ~ "Albumin-Cre",
      TRUE ~ "CD19-Cre"
    ),
    comparison = factor(comparison, levels = c("Albumin-Cre", "Adipo-Cre", "CD19-Cre")),
    group = factor(group, levels = c("Other", "Endoplasmic reticulum", "Signal peptide")),
    column = factor(column, levels = rev(c("Other", "Endoplasmic reticulum", "Signal peptide")))
  ) %>%
  ggplot(
    aes(y = comparison, fill = group)
  ) +
  geom_bar(position = "fill", show.legend = TRUE, color = "black", size = LINE_WIDTH, width = 0.65) +
  facet_rep_grid(rows = vars(column), repeat.tick.labels = TRUE) +
  scale_fill_manual(values = c(
    "Signal peptide" = "cornflowerblue",
    "Endoplasmic reticulum" = "hotpink4", "Other" = "grey"
  ), name = NULL)

percent_barplot_theme(obj) +
  ggtitle("% of proteins significantly enriched \nin Cre+ samples") +
  theme(strip.text = element_blank(), panel.spacing.y = unit(0.2, "cm"))

save_plot(
  "s1j_summary",
  ht = 2,
  wd = 2.49
)
```

# Figure 2

## 2G: Volcano plots

```{r, fig.width=4.5, fig.height=4.5}
# read list of proteins to highlight
highlight_proteins <- "reference_data/new_fig2_highlights.csv" %>%
  read_csv(show_col_types = FALSE) %>%
  mutate(key = paste(protein, tissue, comparison, sep = "_")) %>%
  pull(key)

df <- dep_path %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    experiment %in% c("20220714_EV1_98", "20220807_EV1_101"),
    comparison %in% c("fast vs. basal", "LPS vs. basal")
  ) %>%
  mutate(
    tissue = case_when(Cre == "Albumin" ~ "Hepatocytes", TRUE ~ "Adipocytes"),
    `Entry Name` = entry_name, group = Regulation, log2FC = log2_FC, comparison = case_when(comparison == "fast vs. basal" ~ "fasting", TRUE ~ "LPS")
  ) %>%
  add_alias()

# build a annotation dataframe iteratively
rows <- list()
for (comp in unique(df$comparison)) {
  for (mouse_tissue in unique(df$tissue)) {
    tissue_name <- case_when(mouse_tissue == "Hepatocytes" ~ "liver", TRUE ~ "fat")
    exp <- df %>% filter(comparison == comp, tissue == mouse_tissue)
    n_up <- exp %>%
      filter(Regulation == "Significant Up") %>%
      nrow()
    n_down <- exp %>%
      filter(Regulation == "Significant Down") %>%
      nrow()
    up_row <- data.frame(
      text = paste(n_up, "up \nin", comp, tissue_name, " "),
      x_pos = Inf,
      hjustvar = 1,
      proteins = n_up,
      tissue = mouse_tissue,
      comparison = comp
    )
    down_row <- data.frame(
      text = paste(" ", n_down, "down\n. in", comp, tissue_name),
      x_pos = -Inf,
      hjustvar = -0,
      proteins = n_down,
      tissue = mouse_tissue,
      comparison = comp
    )
    rows <- append(rows, list(up_row, down_row))
  }
}
annotation_df <- bind_rows(rows)

label_df <-
  df %>%
  mutate(key = paste(alias, tissue, comparison, sep = "_")) %>%
  filter(key %in% highlight_proteins, Regulation %in% c("Significant Up", "Significant Down"))

x_lim <- max(abs(df$log2_FC))

df %>%
  mutate(Regulation = factor(Regulation, levels = names(REGULATION_COLORS))) %>%
  arrange(Regulation) %>%
  volcano_plot_base(
    params = list(
      stroke = LINE_WIDTH,
      show_legend = FALSE,
      palette = REGULATION_COLORS, alpha_palette = ALPHA_PALETTE
    ),
    left_annotation = "",
    right_annotation = ""
  ) +
  geom_text(
    data = annotation_df,
    aes(
      x = x_pos,
      y = Inf,
      hjust = hjustvar,
      vjust = 1.25,
      label = text
    ),
    inherit.aes = FALSE,
    size = FONT_SIZE_MM,
    fontface = "italic",
    lineheight = 0.95
  ) +
  geom_text_repel(data = label_df %>% filter(log2_FC > 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = 5.5 * 0.352778, xlim = c(1.5, x_lim), nudge_x = 5, nudge_y = 1, segment.color = "grey70") +
  geom_text_repel(data = label_df %>% filter(log2_FC < 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = 5.5 * 0.352778, xlim = c(-x_lim, 1.5), nudge_x = -5, nudge_y = 1, segment.color = "grey70") +
  facet_grid(cols = vars(tissue), rows = vars(comparison), axes = "all", axis.labels = "all") +
  xlim(-x_lim, x_lim) +
  ylim(0, max(df$`-log10_pval`) + 1) +
  xlab(expression("log"[2] * "(fold-change)")) +
  theme(strip.text.y = TEXT_ELEMENT)



save_plot(fn = "2g_volcano_plots", ht = 4.5, wd = 4.5)
```

## 2H GO-term analysis

```{r, fig.width=2.6, fig.height=3.1}
facetted_go_term <-
  function(file_paths,
           comparison_1,
           comparison_2,
           go_class = "biological_process", filter_direction = FALSE) {
    # read concat go results
    df <-
      paste0(
        PIPELINE_RESULTS_PATH,
        "turboid_go_term_analysis_ref_list.csv"
      ) %>%
      read_csv(show_col_types = FALSE) %>%
      filter( # filter to relevant results
        experiment %in% file_paths
      ) %>%
      filter(
        (
          grepl(comparison_1, comparison) | grepl(comparison_2, comparison)
        ),
        direction != "up_and_down",
        class == go_class
      )

    if (filter_direction) {
      df <- df %>% filter(direction == "up")
    }

    df <- df %>% filter( # stringency filters
      p_fdr_bh < 0.05,
      n_genes > 4
    ) %>%
      # metadata
      mutate(
        tissue = recode(experiment, !!!setNames(names(file_paths), file_paths)),
        comparison = str_split(comparison, " ") %>% map_chr(1),
        comparison = factor(
          comparison,
          levels = c(
            str_split(comparison_1, " ") %>% map_chr(1),
            str_split(comparison_2, " ") %>% map_chr(1)
          )
        ),
        `-log10(FDR)` = case_when(direction == "up" ~ `-log10(FDR)`, TRUE ~ -1 *
          `-log10(FDR)`),
        term = str_wrap(term, 30)
      )
    plt <- df %>%
      # dot plot
      ggplot(aes(
        x = `-log10(FDR)`,
        y = reorder_within(
          term,
          by = `-log10(FDR)`,
          within = comparison,
          fun = min
        ),
        size = n_genes,
        fill = direction
      )) +
      geom_vline(
        xintercept = 0,
        color = "black",
        size = LINE_WIDTH
      ) +
      geom_point(
        shape = 21,
        stroke = LINE_WIDTH,
        color = "black"
      ) +
      facet_grid(
        rows = vars(comparison),
        cols = vars(tissue),
        space = "free",
        scales = "free_y"
      ) +
      scale_fill_manual(values = c("up" = "indianred2", "down" = "steelblue2")) +
      scale_size_continuous(range = c(1, 2.7), name = NULL) +
      scale_y_reordered() +
      turboid_theme() +
      theme(
        legend.position = "bottom",
        strip.text.y = element_text(
          color = "black",
          size = FONT_SIZE,
          family = "Arial"
        ),
        panel.grid.major.y = element_line(color = "grey90", size = LINE_WIDTH),
        legend.byrow = TRUE,
        panel.spacing = unit(1, "mm"),
        axis.text.y = element_text(
          size = 6,
          family = FONT_FAMILY,
          color = "black"
        )
      ) +
      labs(x = expression("log"[10] * "(FDR)"), y = NULL, ) +
      scale_x_continuous(
        expand = expansion(mult = c(0.2, 0.2)),
        labels = function(x) {
          abs(x)
        }
      ) +
      guides(fill = FALSE)

    print(plt)
    return(df)
  }

facetted_go_term(
  file_paths = list(
    "Hepatocytes" = "20220714_EV1_98",
    "Adipocytes" = "20220807_EV1_101"
  ),
  comparison_1 = "fast vs. basal",
  comparison_2 = "LPS vs. basal"
)

save_plot("2h_go_term_ref_list",
  ht = 3.1,
  wd = 2.6
)
```

## 2I Go term Correlation plot

```{r, fig.width=2.2635, fig.height=4}
get_study_genes <- function(go_term_name) {
  # helper method to pull a list of
  # genes related to a GO term
  study_genes <- go_path %>%
    read_csv(show_col_types = FALSE) %>%
    filter(term == go_term_name) %>%
    mutate(gene_list = str_extract_all(study_genes, "'[^']+'") %>%
      map(~ str_remove_all(.x, "'"))) %>%
    tidyr::unnest_longer(col = gene_list) %>%
    pull(gene_list) %>%
    unique()
  return(study_genes)
}

go_term_correlation <- function(cell_type = "Hepatocytes", upper_limit = 6.4, lower_limit = -2.8, fn = "zHepatocyte_correlation_plot", label_genes = c(
                                  "SAA2", "SAA1", "IRG1", "LPIN1", "CP4AE", "CP4AA", "CES1D", "APOA4", "CP7A1", "SERPINA3N"
                                )) {
  file_paths <- list(
    "Hepatocytes" = "20220714_EV1_98",
    "Adipocytes" = "20220807_EV1_101", fn = "2I_correlation_plot"
  )

  
  go_term_name_1 <- "inflammatory response"
  go_term_name_2 <- "cell adhesion"

  alpha_palette <- c(
    setNames(0.6, go_term_name_1),
    setNames(0.6, go_term_name_2),
    both = 0.7,
    other = 0.4
  )

  fill_palette <- c(
    setNames("#80c5ed", go_term_name_2),
    setNames("#459343", go_term_name_1),
    both = "#edb180",
    other = "grey80"
  )

  study_genes_1 <- get_study_genes(go_term_name_1)
  study_genes_2 <- get_study_genes(go_term_name_2)

  # make a correlation plot

  dep_path %>%
    read_csv(show_col_types = FALSE) %>%
    filter(
      experiment == file_paths[cell_type],
      comparison %in% c("fast vs. basal", "LPS vs. basal")
    ) %>%
    pivot_wider(
      id_cols = c(entry_name, gene_name),
      values_from = log2_FC,
      names_from = comparison
    ) %>%
    mutate(`Entry Name` = entry_name) %>%
    add_alias() %>%
    drop_na() %>%
    mutate(
      group =
        case_when(
          (gene_name %in% study_genes_1) & (gene_name %in% study_genes_2) ~ "both",
          (gene_name %in% study_genes_1) ~ go_term_name_1,
          (gene_name %in% study_genes_2) ~ go_term_name_2,
          TRUE ~ "other"
        )
    ) %>%
    arrange(desc(group)) -> df



  arc_df <- df %>% filter(group == "both")
  arc_df <- arc_df %>%
    tidyr::uncount(2) %>% # duplicate each row
    mutate(
      start = rep(c(0, pi), times = nrow(arc_df)),
      end = rep(c(pi, 2 * pi), times = nrow(arc_df)),
      fill = rep(c(go_term_name_1, go_term_name_2), times = nrow(arc_df)),
      r0 = 0, # inner radius (center)
      r = 0.11826955524 # outer radius (size of the point)
    )

  plt <- df %>%
    ggplot(aes(x = `fast vs. basal`, y = `LPS vs. basal`, fill = group, alpha = group, label = alias)) +
    geom_vline(xintercept = 0, size = LINE_WIDTH) +
    geom_hline(yintercept = 0, size = LINE_WIDTH) +
    geom_segment(
      data = data.frame(),
      aes(
        x = lower_limit,
        y = lower_limit,
        xend = upper_limit,
        yend = upper_limit
      ),
      size = LINE_WIDTH,
      inherit.aes = FALSE
    ) +
    geom_point(
      data = df,
      shape = 21,
      size = 1.7,
      stroke = 0,
      # stroke = LINE_WIDTH,
      color = "black",
      # alpha = 0.3,
      show.legend = TRUE
    ) +
    geom_text_repel(
      data = df %>% filter(alias %in% label_genes),
      size = FONT_SIZE_MM,
      show.legend = FALSE,
      color = "black",
      alpha = 1,
      segment.size = LINE_WIDTH,
      min.segment.length = 0,
      family = FONT_FAMILY
    ) +
    ggtitle(paste0(
      gsub("s", "", cell_type),
      " LPS and fasting\ntreatment correlation (",
      format(nrow(df), big.mark = ",", scientific = FALSE),
      " proteins)"
    )) +
    scale_fill_manual(
      values = fill_palette,
      name = NULL
    ) +
    scale_alpha_manual(
      values = alpha_palette,
      name = NULL
    ) +
    guides(alpha = NULL, stroke = NULL, color = NULL, fill = guide_legend(nrow = 2)) +
    labs(
      x = expression("log"[2] * "(fast/basal)"),
      y = expression("log"[2] * "(LPS/basal)")
    ) +
    turboid_theme() +
    theme(legend.position = "top", legend.byrow = TRUE, aspect.ratio = 1, legend.margin = margin(b = -15), legend.key = element_blank()) +
    scale_x_continuous(expand = expansion(mult = c(0, 0)), limits = c(lower_limit, upper_limit)) +
    scale_y_continuous(expand = expansion(mult = c(0, 0)), limits = c(lower_limit, upper_limit))

  print(plt)

  save_plot(fn, wd = 2.2635, ht = 4)
  return(df)
}

# HEPATOCYTE
df1 <- go_term_correlation(
  label_genes = c("SAA2", "SAA1", "IRG1",  "CP4AE",  "APOA4", "SERPINA3N", "FGL1","5NTD", "FND3B",
                  # new genes requested by CW
                  "LICH", "PDIA4", "CFH"),
  fn = "2l_goterm_correlation_plot"
  )


# ADIPOCYTE
df <- go_term_correlation(
  "Adipocytes", 
  upper_limit = 4, 
  lower_limit = -3.5, 
  fn = "s2e_goterm_correlation_plot", 
  label_genes = c("SERPINA3N", "C3", "MYO5A", "GBP5", "CD47", "5NTD", "FND3B", 
                  # new genes requested by CW
                  "TSP2", "THBS1", "GAS6"))

df1 %>% arrange(by = `fast vs. basal`) %>% filter(group == "both")

```

```{r}
df1 %>%filter(group == "cell adhesion") %>% arrange(desc(abs(`LPS vs. basal`)))
```


## S2A: overlap enrichment plot

```{r, fig.width=4, fig.height=2.5}
paste0(PIPELINE_RESULTS_PATH, "go_overlap_results.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    class == "biological_process",
    p_fdr_bh < 0.05,
    n_genes > 4
  ) %>%
  mutate(
    # clean intersect names
    intersect = paste(set_1, set_2),
    intersect = gsub("Significant Down", "down in", intersect),
    intersect = gsub("Significant Up", "up in", intersect),
    intersect = gsub("vs. basal_", "", intersect),
    intersect = gsub(" down", " and down", intersect),
    intersect = gsub(" up", " and up", intersect),
    intersect = gsub("Adipocytes", "fat", intersect),
    intersect = gsub("Hepatocytes", "liver", intersect),
    intersect = gsub("_", " ", intersect)
  ) -> df

intersects_to_highlight <- c(
  "down in LPS fat and down in fast fat",
  "down in LPS liver and down in LPS fat",
  "down in LPS liver and down in fast liver"
)
df %>%
  filter(
    intersect %in% intersects_to_highlight
  ) %>%
  mutate(intersect = factor(intersect, levels = intersects_to_highlight)) %>%
  ggplot(aes(x = `-log10(FDR)`, y = reorder_within(term, by = `-log10(FDR)`, within = intersect), size = n_genes)) +
  geom_point(shape = 21, fill = POINT_FILL, stroke = LINE_WIDTH) +
  facet_rep_grid(space = "free", rows = vars(intersect), scales = "free_y") +
  turboid_theme() +
  scale_y_reordered() +
  theme(strip.text.y = element_text(size = FONT_SIZE, color = "black", family = FONT_FAMILY, angle = 0), legend.position = "bottom", panel.spacing.y = unit(0, "cm"), panel.border = element_blank(), axis.line.x = AXIS_LINE, axis.line.y = AXIS_LINE) +
  scale_size_continuous(range = c(1, 3)) +
  labs(
    x = expression("-log"[10] * "(FDR)"), y = NULL
  ) +
  scale_x_continuous(expand = expansion(mult = c(0.2, 0.2)))
save_plot("s2a_go_term", wd = 4, ht = 2.5)
```

## S2 correlation with margins

```{r, fig.width=2, fig.height=4}
correlation_plot <-
  function(timepoints,
           sample_type,
           min,
           max,
           correlation_palette,
           num_top = 6,
           x_lab,
           y_lab,
           drop = NULL,
           top = c()) {
    # constants for defining position of margins
    margin_factor <- 0.85
    margin_position <- min * margin_factor
    missing_point_value <- (min + margin_position) / 2

    combined_df <- NULL
    for (timepoint in names(timepoints)) {
      df <-
        read_experiment(timepoints[timepoint], sample_type[timepoint])
      #print("df")
      #print(colnames(df))
      df <- df %>%
        dplyr::select(
          starts_with("log2_FC"),
          starts_with("-log10_pval"),
          uniprot_id,
          `Entry Name`
        ) %>%
        add_alias() %>%
        mutate(time_point = timepoint) %>%
        dplyr::select(-contains("cre+")) %>%
        dplyr::select(-contains(drop))
      print(timepoints[timepoint])
      print("HPGD" %in% df$alias)
      colnames(df) <-
        c(
          "log2_FC",
          "log10_pval",
          "uniprot_id",
          "Entry Name",
          "protein",
          "alias",
          "time_point"
        )
      combined_df <- rbind(df, combined_df)
    }

    log_threshold <- -log10(0.05)


    wide_df <- combined_df %>%
      pivot_wider(
        names_from = time_point,
        values_from = c(log2_FC, log10_pval)
      )

    
    combined_df <- wide_df %>%
      mutate(
        significance = case_when(
          (log10_pval_x > log_threshold) &
            (log10_pval_y > log_threshold) ~ names(correlation_palette[4])[1],
          (log10_pval_y > log_threshold) ~ names(correlation_palette[2])[1],
          (log10_pval_x > log_threshold) ~ names(correlation_palette[1])[1],
          TRUE ~ names(correlation_palette[3])[1]
        )
      ) %>%
      mutate(
        #significance = factor(significance, levels = names(correlation_palette)),
        dist_from_orig = sqrt(log2_FC_x^2 + log2_FC_y^2),
        distance_from_identity = abs(log2_FC_x - log2_FC_y)
      ) 

    # calculate pearson's correlation from complete cases
    pearson_r <- cor(combined_df$log2_FC_x, combined_df$log2_FC_y, use = "complete.obs") %>%
      round(digits = 2)


    print(max(combined_df$log2_FC_x, na.rm = TRUE))
    print(max(combined_df$log2_FC_y, na.rm = TRUE))
    print(min(combined_df$log2_FC_x, na.rm = TRUE))
    print(min(combined_df$log2_FC_y, na.rm = TRUE))

    combined_df <- combined_df %>%
      # replace missing values with values on the margins
      replace_na(list(log2_FC_x = missing_point_value, log2_FC_y = missing_point_value))

    # pull list of proteins to give text labels
    significant_no_missing <- combined_df %>%
      filter(
        significance != "Not significant",
        log2_FC_x != missing_point_value,
        log2_FC_y != missing_point_value
      )
    label_data <- rbind(
      # top by distance from identity
      significant_no_missing %>%
        arrange(distance_from_identity) %>%
        tail(num_top),
      # top by distance from origin
      significant_no_missing %>%
        arrange(dist_from_orig) %>%
        tail(num_top),
      # top only quantified at x
      combined_df %>%
        arrange(abs(log2_FC_x)) %>%
        filter(
          significance != "Not significant",
          (log2_FC_y == missing_point_value)
        ) %>%
        tail(num_top / 2),
      # top only quantified at y
      combined_df %>%
        arrange(abs(log2_FC_y)) %>%
        filter(
          significance != "Not significant",
          (log2_FC_x == missing_point_value)
        ) %>%
        tail(num_top / 2)
    ) %>% distinct()
    
    if (length(top) > 0){
      label_data <- combined_df %>% filter(significance != "Not significant", alias %in% top)
    }
    
    print(top[!top %in% unique(label_data$alias)])
    print("CAVIN2" %in% combined_df$alias)
    print("SDPR" %in% combined_df$alias)

    plot <- combined_df %>%
      # sort so labeled points are stacked on top
      mutate(z_order = alias %in% unique(label_data$alias)) %>%
      arrange(z_order) %>%
      ggplot(aes(
        x = log2_FC_x,
        y = log2_FC_y,
        fill = significance,
        label = alias
      )) +
      # margin lines
      geom_hline(
        yintercept = margin_position,
        size = LINE_WIDTH,
        color = "black"
      ) +
      geom_vline(
        xintercept = margin_position,
        size = LINE_WIDTH,
        color = "black"
      ) +
      # origin lines
      geom_hline(
        yintercept = 0,
        color = "grey90",
        size = LINE_WIDTH
      ) +
      geom_vline(
        xintercept = 0,
        color = "grey90",
        size = LINE_WIDTH
      ) +
      # diagonal boundary lines
      geom_segment(
        data = data.frame(),
        aes(
          x = c(margin_position, margin_position, margin_position + 1),
          y = c(margin_position + 1, margin_position, margin_position),
          xend = c(max - 1, max, max),
          yend = c(max, max, max - 1),
          linetype = c("dashed", "solid", "dashed")
        ),
        size = LINE_WIDTH,
        inherit.aes = FALSE,
        show.legend = FALSE,
        color = "black"
      ) +
      # scatterplot
      geom_point(
        shape = 21,
        stroke = 0,
        alpha = 0.55,
        size = 1.4,
      ) +
      # protein labels
      geom_text_repel(
        data = label_data,
        size = 1.94028,
        family = FONT_FAMILY,
        min.segment.length = 0,
        #force = 3,
        segment.size = LINE_WIDTH,
        max.overlaps = Inf,
        #nudge_y = -2,
        #nudge_x = 2,
        show.legend = FALSE#,
        #segment.curvature = -0.1,
      #segment.ncp = 3,
      #segment.angle = 45
      ) +
      turboid_theme() +
      theme(
        aspect.ratio = 1,
        # 20 lines of legend formatting
        legend.position = "top",
        legend.text = element_text(
          size = 6,
          color = "black",
          family = "Arial",
          margin = margin(l = 0)
        ),
        legend.box.background = element_blank(),
        legend.justification.top = "top",
        legend.justification = "center",
        legend.box.just = "center",
        legend.key = element_blank(),
        legend.margin = margin(l = -5, b = -5.5),
        legend.box.margin = margin(l = -5, b = -0.8),
        legend.key.spacing.y = unit(-0.9, "cm"),
        legend.key.spacing.x = unit(-0.1, "cm")
      ) +
      guides(fill = guide_legend(nrow = 2, override.aes = list(alpha = 1))) +
      labs(
        x = x_lab,
        y = y_lab
      ) +
      scale_fill_manual(values = correlation_palette, name = NULL) +
      scale_x_continuous(expand = expansion(mult = 0), limits = c(min, max)) +
      scale_y_continuous(expand = expansion(mult = 0), limits = c(min, max)) +
      scale_linetype_manual(values = c("dashed" = "dashed", "solid" = "solid")) +
      geom_text(
        mapping = aes(
          x = min * 0.6,
          y = max * 0.85,
        ),
        label = paste("R = ", as.character(pearson_r)),
        inherit.aes = FALSE,
        data = data.frame(),
        size = 1.94028,
        family = FONT_FAMILY
      )

    print(plot)
  }

correlation_min <- -5
correlation_max <- 6.4

not_significant <- "grey80"

# liver vs plasma LPS stimulation
correlation_plot(
  timepoints = c(
    "x" = "20220714_EV1_98", # x is liver
    "y" = "20220807_EV1_101" # y is fat
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "tissue"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "liver p < 0.05" = "#d6e5b3",
    "iWAT p < 0.05" = "#75c489",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#5d8f70"
  ),
  num_top = 6,
  x_lab = expression("liver, log"[2] * "(LPS/basal)"),
  y_lab = expression("iWAT, log"[2] * "(LPS/basal)"),
  drop = "fast",
  top = c("IFIT1","SAMP","SERPINA3N","EST1","STEA4","IRG1", 'FAM20C', 'EST1C', 'IFIH1', 'HEMO', 'EST2A', 'LAMA4', 'GBP5', 'CTNA1', 'CDS2', 'LPL')
)


save_plot(
  fn = "s2g_correlation",
  wd = 2,
  ht = 4
)

wide_df <- correlation_plot(
  timepoints = c(
    "x" = "20220714_EV1_98", # x is liver
    "y" = "20220807_EV1_101" # y is fat
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "tissue"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "liver p < 0.05" = "#c4dfec",
    "iWAT p < 0.05" = "#85c6ed",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#4482c3"
  ),
  num_top = 5,
  x_lab = expression("liver, log"[2] * "(fast/basal)"),
  y_lab = expression("iWAT, log"[2] * "(fast/basal)"),
  drop = "LPS",
  top = c("LIFR","LPIN1","SAA1","SAA2","TSP2",'FAM20C', 'EST1C', 'IFIH1', 'HEMO', 'EST2A', 'LAMA4', 'GBP5', 'CTNA1', 'CDS2', 'LPL')
)

save_plot(
  fn = "s2h_correlation",
  wd = 2,
  ht = 4
)

```

## 2J heatmaps

```{r}
get_plot_width <- function(n) {
  # return(10)
  return(0.0708 * n + 1.3220833333)
  # return ((0.02 * n)  + 0.898)
}
prepare_fc_data <- function(experiment, control_name, filter_to_sig = FALSE) {
  experiment <- experiment %>%
    mutate(protein = gsub(pattern = "_MOUSE", "", `Entry Name`)) %>%
    add_alias()
  # filter proteome to genes to display
  df <- experiment %>%
    dplyr::select(uniprot_id, contains("Regulation") & contains(control_name)) %>%
    pivot_longer(cols = contains("Regulation") & !contains("cre+")) %>%
    filter((value == "Significant Up") | (value == "Significant Down"))
  uniprot_list <- df %>%
    pull(uniprot_id) %>%
    unique()

  if (filter_to_sig) {
    experiment <- experiment %>%
      filter(uniprot_id %in% uniprot_list)
  }

  heatmap_data <- experiment %>%
    column_to_rownames("alias") %>%
    # select signal intensity columns
    dplyr::select(contains("cre+_") & !contains("ratio")) %>%
    dplyr::select(sort(names(.)))

  # sample names containing "basal" or ctrl name
  basal_samples <- grepl(control_name, colnames(heatmap_data))

  fold_change <- heatmap_data / rowMeans(heatmap_data[, basal_samples])

  fold_change %>%
    # drop basal samples
    dplyr::select(-c(colnames(heatmap_data)[basal_samples])) %>%
    # sort columns so each organ table has the same column order
    dplyr::select(order(colnames(.))) %>%
    as.matrix() %>%
    # log2 transform
    log2() %>%
    as.data.frame() %>%
    filter(apply(., 1, function(x) all(is.finite(x)))) %>%
    as.matrix() %>%
    t() %>%
    return()
}


fc_heatmap <- function(experiment, output_filename, width, height, control_name = "basal", group_colors = c("#7FC5ED", "#459343"), n_cell_types = 2, labels = c("Fast", "LPS"), col_name_rot = 45, col_names_size, save_file = TRUE) {
  heatmap_data <- experiment
  # font settings
  text_graphics <- gpar(fontsize = 6, fontfamily = "Arial")

  column_gap <- unit(0.5, "mm")
  legend_height <- unit(2, "mm")
  ht_opt(COLUMN_ANNO_PADDING = column_gap)
  ht_opt(HEATMAP_LEGEND_PADDING = column_gap)
  ht_opt(TITLE_PADDING = column_gap)


  # get condition labels from sample names
  heatmap_data %>%
    rownames() %>%
    # condition is sample name before the first "_"
    lapply(function(x) str_split_1(x, "_")[1]) -> metadata

  metadata %>%
    unlist() %>%
    recode(!!!c("fast" = "Fasting")) -> condition_labels

  metadata %>%
    lapply(function(x) str_split_1(x, " ")[1]) %>%
    unlist() -> cell_type_labels



  if (n_cell_types == 2) {
    # For 2 cell types, get the first cell type's LPS rows
    # The first LPS group should be the first occurrence of "LPS" label
    lps_rows <- which(condition_labels == "LPS")
    if (length(lps_rows) > 0) {
      # Take only the first half of LPS rows (first cell type)
      first_cell_lps_rows <- lps_rows[1:(length(lps_rows) / 2)]
      lps_means <- colMeans(heatmap_data[first_cell_lps_rows, , drop = FALSE])
      # Sort columns by descending mean values (highest to lowest)
      col_order <- order(lps_means, decreasing = TRUE)
      # Reorder the heatmap data
      heatmap_data <- heatmap_data[, col_order]
    }
  } else {
    # For single cell type, use all LPS rows
    lps_rows <- which(condition_labels == "LPS")
    if (length(lps_rows) > 0) {
      lps_means <- colMeans(heatmap_data[lps_rows, , drop = FALSE])
      # Sort columns by descending mean values (highest to lowest)
      col_order <- order(lps_means, decreasing = TRUE)
      # Reorder the heatmap data
      heatmap_data <- heatmap_data[, col_order]
    }
  }


  # build heatmap condition color labels
  cond_annotation <- rowAnnotation(
    empty = anno_empty(border = FALSE, width = unit(4, "mm")),
    simple_anno_size_adjust = TRUE,
    condition = anno_block(
      gp = gpar(fill = group_colors, col = "transparent", alpha = 0.6),
      labels = rep(labels, n_cell_types),
      labels_gp = gpar(fontsize = 6, fontfamily = "Arial"),
      which = "row",
      width = unit(4, "mm")
    )
  )
  organ <- "liver"
  main_heatmap <- heatmap_data %>%
    Heatmap(
      name = "heatmap",
      cluster_rows = FALSE,
      # cluster within slices, but not across
      cluster_columns = FALSE,
      cluster_row_slices = TRUE,
      row_title = NULL,
      show_row_dend = FALSE,
      show_column_dend = FALSE,
      column_title_gp = text_graphics,
      col = colorRamp2(c(-2, 0, 2), c("blue", "white", "red")),
      row_split = condition_labels,
      left_annotation = cond_annotation,
      show_row_names = FALSE,
      column_gap = column_gap,
      row_gap = unit(0.5, "mm"),
      column_names_gp = gpar(fontsize = col_names_size, fontfamily = "Arial"),
      column_names_side = "bottom",
      column_names_rot = col_name_rot,
      heatmap_legend_param = list(
        title = substitute(
          paste("log"[2], "(FC from ", m, ")"), list(m = control_name)
        ),
        legend_height = legend_height,
        title_gp = text_graphics,
        labels_gp = text_graphics,
        border = "transparent",
        grid_width = unit(2, "mm")
      ),
    )

  if (save_file) {
    pdf(
      file = paste0(PLOT_RESULTS_PATH, output_filename),
      width = width,
      height = height
    )

    set.seed(333)
    draw(main_heatmap, ht_gap = column_gap)
    dev.off()
  } else {
    draw(main_heatmap, ht_gap = column_gap)
  }
  return(main_heatmap)
}

group_block_anno <- function(
    group, empty_anno, gp = gpar(),
    label = NULL, label_gp = gpar()) {
  # adding group labels to multiple row splits

  seekViewport(qq("annotation_@{empty_anno}_@{max(group)}"))
  loc1 <- deviceLoc(x = unit(0, "npc"), y = unit(0, "npc"))
  seekViewport(qq("annotation_@{empty_anno}_@{min(group)}"))
  loc2 <- deviceLoc(x = unit(1, "npc"), y = unit(1, "npc"))

  seekViewport("global")
  grid.rect(loc1$x, loc1$y,
    width = loc2$x - loc1$x, height = loc2$y - loc1$y,
    just = c("left", "bottom"), gp = gp
  )
  if (!is.null(label)) {
    grid.text(label, x = (loc1$x + loc2$x) * 0.5, y = (loc1$y + loc2$y) * 0.5, gp = label_gp, rot = 90)
  }
}

go_terms <- c("immune system process", "extracellular matrix organization")


cell_configs <- list(
  "Adipocytes" = list(experiment = "20220807_EV1_101", plot_width = 7.5),
  "Hepatocytes" = list(experiment = "20220714_EV1_98", plot_width = 5.5)
)
for (go_term_name in go_terms) {
  for (cell_type in names(cell_configs)) {
    config <- cell_configs[[cell_type]]

    gt <- get_study_genes(go_term_name)
    df1 <- read_experiment(config$experiment, "tissue") %>%
      filter(gene_name %in% gt) %>%
      prepare_fc_data("basal", filter_to_sig = TRUE)
    print(ncol(df1))
    plot_width <- get_plot_width(ncol(df1))
    print(plot_width)
    pdf(
      file = paste0(
        PLOT_RESULTS_PATH,
        paste0("s2_", go_term_name, cell_type, ".pdf")
      ),
      width = plot_width,
      height = 1
    )

    df1 %>% fc_heatmap(
      output_filename = "aa",
      n_cell_types = 1,
      col_names_size = 5,
      col_name_rot = 90,
      save_file = FALSE
    )
    lbl_gp <- gpar(
      col = "black",
      fontsize = 6,
      rot = 0,
      fontfamily = FONT_FAMILY
    )
    group_block_anno(
      c(1, 2),
      "empty",
      gp = gpar(fill = "grey90", col = "white"),
      label = cell_type,
      label_gp = lbl_gp
    )
    dev.off()
  }
}
```

### Heatmap with both cell types

```{r}
go_term_name <- "vesicle-mediated transport"
go_term_name <- "cell adhesion"

for (go_term_name in c("protein glycosylation", "protein folding", "cell adhesion")) {
  gt <- get_study_genes(go_term_name)
  print(gt)
  # gt <- c("Fgb","Fgg","C3","C4b","Fga","Apoa1","C6","Stat1","Apcs","Apoa4","Tfrc","Pml","Hp","Rbp4")
  # gt <- c("Itgb1","Col18a1","St3gal4","Sorbs3","Slc4a1","Itgb5","Fndc3b","Siglec1","Ptprd","Gpc4","Dmd","Tgm2","Afdn","Parva")
  df2 <- read_experiment("20220714_EV1_98", "tissue") %>%
    filter(gene_name %in% gt) %>%
    prepare_fc_data("basal")
  rownames(df2) <- paste("Hepatocytes", rownames(df2))
  df1 <- read_experiment("20220807_EV1_101", "tissue") %>%
    filter(gene_name %in% gt) %>%
    prepare_fc_data("basal")
  rownames(df1) <- paste("Adipocytes", rownames(df1))
  df2 <- df2[, colnames(df2)[colnames(df2) %in% colnames(df1)]]
  df1 <- df1[, colnames(df2)]
  mat <- rbind(df1, df2)

  hepatocytes_lps_rows <- grep("^Hepatocytes LPS", rownames(mat))
  col_means <- colMeans(mat[hepatocytes_lps_rows, ])
  mat <- mat[, order(col_means, decreasing = TRUE)]


  pdf(
    file = paste0(PLOT_RESULTS_PATH, paste0("s2j_2celltypes_", go_term_name, ".pdf")),
    width = get_plot_width(ncol(mat)),
    # width = 10,
    height = 1.53
  )
  print(ncol(mat))
  mat %>%
    as.data.frame() %>%
    fc_heatmap(output_filename = "aa", col_names_size = 5, save_file = FALSE, col_name_rot = 90)

  lbl_gp <- gpar(col = "black", fontsize = 6, rot = 0, fontfamily = FONT_FAMILY)
  group_block_anno(c(1, 2), "empty", gp = gpar(fill = "grey90", col = "white"), label = "Adipocytes", label_gp = lbl_gp)
  group_block_anno(c(3, 4), "empty", gp = gpar(fill = "grey90", col = "white"), label = "Hepatocytes", label_gp = lbl_gp)
  dev.off()
}
mat
```

### Heatmap with one cell type

```{r}
go_terms <- c("immune system process", "extracellular matrix organization")


cell_configs <- list(
  "Adipocytes" = list(experiment = "20220807_EV1_101", plot_width = 7.5),
  "Hepatocytes" = list(experiment = "20220714_EV1_98", plot_width = 5.5)
)
for (go_term_name in go_terms) {
  for (cell_type in names(cell_configs)) {
    config <- cell_configs[[cell_type]]

    gt <- get_study_genes(go_term_name)
    df1 <- read_experiment(config$experiment, "tissue") %>%
      filter(gene_name %in% gt) %>%
      prepare_fc_data("basal", filter_to_sig = TRUE)
    print(ncol(df1))
    plot_width <- (0.078 * ncol(df1)) + 0.898
    print(plot_width)
    pdf(
      file = paste0(
        PLOT_RESULTS_PATH,
        paste0("s2_", go_term_name, cell_type, ".pdf")
      ),
      width = plot_width,
      height = 1
    )

    df1 %>% fc_heatmap(
      output_filename = "aa",
      n_cell_types = 1,
      col_names_size = 5,
      col_name_rot = 90,
      save_file = FALSE
    )
    lbl_gp <- gpar(
      col = "black",
      fontsize = 6,
      rot = 0,
      fontfamily = FONT_FAMILY
    )
    group_block_anno(
      c(1, 2),
      "empty",
      gp = gpar(fill = "grey90", col = "white"),
      label = cell_type,
      label_gp = lbl_gp
    )
    dev.off()
  }
}
```

# Figure 3

## 3B: Outcyte Percent barplot

```{r, fig.width=2.2, fig.height=1.1}
alb_plasma <- read_experiment("20221129_EV1_136", "serum") %>%
  dplyr::select(uniprot_id, Outcyte) %>%
  mutate(experiment = "Albumin\nCre")
outcyte_df <- read_experiment("20221130_EV1_137", "serum") %>%
  dplyr::select(uniprot_id, Outcyte) %>%
  mutate(experiment = "Adiponectin\nCre") %>%
  rbind(alb_plasma)

outycte_barplot <- function(df) {
  obj <- df %>%
    mutate(Outcyte = replace_na(Outcyte, "NA"), Outcyte = recode(Outcyte, !!!replace_list), Outcyte = factor(Outcyte, levels = rev(names(palette)))) %>%
    ggplot(aes(y = experiment, fill = Outcyte)) +
    geom_bar(
      position = "fill",
      color = "black",
      size = LINE_WIDTH,
      width = 0.65
    ) +
    scale_fill_manual(values = palette) +
    theme(
      legend.key.size = unit(1, "mm"),
      legend.key.height = unit(1, "mm"),
      legend.key.width = unit(1, "mm"),
      legend.key = element_rect(fill = NA)
    )

  plt <- percent_barplot_theme(obj)
  print(plt)
}

outycte_barplot(outcyte_df)

save_plot("3b_percent_barplot", wd = 2.2, ht = 1.1)


```

## 3C: Heatmap

```{r, fig.width=2.5, fig.height=6.7}
fc_heatmap_with_annotation <-
  function(experiment,
           output_filename,
           width,
           height,
           control_name = "basal",
           group_colors = c("#7FC5ED", "#459343")) {
    experiment <- experiment %>%
      mutate(protein = gsub(pattern = "_MOUSE", "", `Entry Name`)) %>%
      add_alias()
    # filter proteome to genes to display
    uniprot_list <- experiment %>%
      dplyr::select(uniprot_id, contains("Regulation") &
        contains(control_name)) %>%
      pivot_longer(cols = contains("Regulation")) %>%
      filter(value == "Significant Up" |
        value == "Significant Down") %>%
      pull(uniprot_id) %>%
      unique()
    experiment <- experiment %>%
      filter(uniprot_id %in% uniprot_list)

    # save outcyte predictions
    outcyte <- experiment %>%
      dplyr::select(alias, Outcyte) %>%
      mutate(
        Outcyte = replace_na(Outcyte, "NA"),
        Outcyte = recode(Outcyte, !!!replace_list),
        Outcyte = factor(Outcyte, levels = rev(names(palette)))
      ) %>%
      column_to_rownames("alias")

    # load Arial font
    loadfonts()
    # font settings
    text_graphics <- gpar(fontsize = 6, fontfamily = "Arial")

    heatmap_data <- experiment %>%
      column_to_rownames("alias") %>%
      # select signal intensity columns
      dplyr::select(contains("cre+_") & !contains("ratio")) %>%
      dplyr::select(sort(names(.)))

    # sample names containing "basal"
    basal_samples <- grepl(control_name, colnames(heatmap_data))

    fold_change <- heatmap_data / rowMeans(heatmap_data[, basal_samples])

    heatmap_data <- fold_change %>%
      # drop basal samples
      dplyr::select(-c(colnames(heatmap_data)[basal_samples])) %>%
      # sort columns so each organ table has the same column order
      dplyr::select(order(colnames(.))) %>%
      as.matrix() %>%
      # log2 transform
      log2() %>%
      as.data.frame() %>%
      filter(apply(., 1, function(x) {
        all(is.finite(x))
      })) %>%
      as.matrix()
    print(heatmap_data)

    column_gap <- unit(0.5, "mm")
    legend_height <- unit(2, "mm")
    ht_opt(COLUMN_ANNO_PADDING = column_gap)
    ht_opt(HEATMAP_LEGEND_PADDING = column_gap)
    ht_opt(TITLE_PADDING = column_gap)


    # get condition labels from sample names
    condition_labels <- heatmap_data %>%
      colnames() %>%
      # condition is sample name before the first "_"
      lapply(function(x) {
        str_split_1(x, "_")[1]
      }) %>%
      unlist() %>%
      recode(!!!c("fast" = "Fasting"))
    # build heatmap condition color labels
    cond_annotation <- HeatmapAnnotation(
      simple_anno_size_adjust = TRUE,
      condition = anno_block(
        gp = gpar(fill = group_colors, col = "transparent"),
        height = unit(2, "mm"),
      )
    )
    organ <- "liver"
    main_heatmap <- heatmap_data %>%
      Heatmap(
        name = "x",
        cluster_rows = TRUE,
        # cluster within slices, but not across
        cluster_columns = FALSE,
        cluster_column_slices = TRUE,
        show_row_dend = FALSE,
        show_column_dend = FALSE,
        column_title_gp = text_graphics,
        col = colorRamp2(c(-2, 0, 2), c("blue", "white", "red")),
        column_split = condition_labels,
        top_annotation = cond_annotation,
        show_column_names = FALSE,
        column_gap = column_gap,
        row_gap = unit(0.5, "mm"),
        # rect_gp = gpar(col = "white", lwd = LINE_WIDTH),
        row_names_gp = gpar(fontsize = 5.5, fontfamily = "Arial"),
        row_names_side = "right",
        heatmap_legend_param = list(
          # label organ in heatmap legend
          title = substitute(
            paste(n, " log"[2], "(FC from ", m, ")"),
            list(n = organ, m = control_name)
          ),
          legend_height = legend_height,
          title_gp = text_graphics,
          labels_gp = text_graphics,
          border = "transparent",
          grid_width = unit(2, "mm")
        ),
      )
    # create a separate heatmap for Outcyte class predictions
    outcyte_heatmap <-
      outcyte[rownames(heatmap_data), , drop = FALSE] %>%
      as.matrix() %>%
      Heatmap(
        name = "class",
        show_column_names = FALSE,
        col = palette,
        column_title_gp = text_graphics,
        heatmap_legend_param = list(
          title = expression("class"),
          legend_height = legend_height,
          title_gp = text_graphics,
          labels_gp = text_graphics,
          border = "transparent",
          grid_width = unit(2, "mm")
        ),
        column_gap = column_gap,
        row_names_side = "right",
        row_names_gp = gpar(fontsize = 5.5, fontfamily = "Arial")
      )

    ht_list <- main_heatmap + outcyte_heatmap
    pdf(
      file = paste0(PLOT_RESULTS_PATH, output_filename),
      width = width,
      height = height
    )

    set.seed(333)
    draw(ht_list, ht_gap = column_gap)
    dev.off()
    draw(ht_list, ht_gap = column_gap)
  }

```

```{r, fig.width=2.2, fig.height=6.65}

read_experiment("20221129_EV1_136", "serum") %>%
  fc_heatmap_with_annotation(output_filename = "3c_heatmap.pdf", width = 2.25, height = 6.65)
```

## 3D: heatmap

```{r, fig.width=2.25, fig.height=5.15}
read_experiment("20221130_EV1_137", "serum") %>% fc_heatmap_with_annotation(output_filename = "3d_heatmap.pdf", width = 2.25, height = 4.95)
```

## 3E: Abundance plot

```{r, fig.width=2, fig.height=4}


abundance_plot <- function(experiment, sample_type, condition, label_proteins) {
  
  # prep published data
published_data <-
  '/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Reference datasets/Published data sets for comparison/Mouse/Absolute plasma concentrations/AbsolutePlasmaConcentrations_forHenry.csv' %>%
  read_csv(show_col_types = FALSE) %>%
  # drop missing data
  rename(
    c(
      "published_concentration" = "Concentration in mouse plasma (pmol ml-1)"
    )
  ) %>%
  select(uniprot_id, published_concentration)

  # prep signal intensity data
  df <- read_experiment(experiment, "serum") %>%
    add_alias() %>%
    # select ID and signal intensity columns
    select(
      c(uniprot_id, alias, Outcyte, Mass),
      contains(condition) & contains("cre+")
    ) %>%
    mutate(Mass = as.numeric(Mass)) %>%
    select(-c(contains("cre-"))) %>%
    # take mean signal intensity
    pivot_longer(cols = -c(uniprot_id, alias, Outcyte, Mass)) %>%
    group_by(uniprot_id, alias, Outcyte, Mass) %>%
    summarise(mean_signal_intensity = mean(value)) %>%
    left_join(published_data, by = "uniprot_id") %>%
    ungroup() %>%
    mutate(rank = order(order(mean_signal_intensity, decreasing = TRUE))) %>%
    arrange(!is.na(mean_signal_intensity), mean_signal_intensity)
  
  df %>% filter(alias == "TSP4") %>% print()

  lbl_df <- df %>% filter(alias %in% label_proteins)

  plt <-
    df %>% ggplot(aes(
      x = rank,
      y = log2(mean_signal_intensity),
      fill = log2(published_concentration),
      color = log2(published_concentration)
    )) +
    geom_point(
      shape = 21,
      color = "black",
      stroke = 0,
      size = 1.5,
      alpha = 0.4,
      show.legend = FALSE
    ) +
    geom_point(
      data = lbl_df,
      shape = 21,
      color = "black",
      stroke = LINE_WIDTH,
      size = 1.5,
      alpha = 1
    ) +
    turboid_theme() +
    scale_y_continuous(breaks = c(15, 20, 25), expand = expansion(mult = c(0.2, 0.1))) +
    theme(aspect.ratio = 1, legend.position = "top", legend.key.height = unit(2.5, "mm"), legend.key.width = unit(4, "mm")) +
    scale_fill_gradient2(midpoint = 7.375, high = "red", low = "blue", na.value = "grey70", limits = c(-1, 16), name = "log2 pmol concentration") +
    scale_color_gradient2(midpoint = 7.375, high = "red", low = "blue", na.value = "grey90", limits = c(-1, 16), name = "log2 pmol concentration") +
    geom_rug(sides = "b", alpha = 0.4, length = unit(2, "mm"), show.legend = FALSE) +
    labs(
      y = substitute(
        paste("log"[2], "(mean signal intensity) ", m, " plasma"), list(m = condition)
      ),
      x = "protein rank"
    ) +
    geom_text_repel(data = lbl_df, mapping = aes(label = alias), size = FONT_SIZE_MM, min.segment.length = 0, segment.size = LINE_WIDTH, box.padding = 0.5, color = "black", max.overlaps = Inf, force = 2, nudge_y = 2)
  print(max(log2(df$published_concentration), na.rm = TRUE))

  print(plt)
}

```

```{r, fig.width=2, fig.height=4}
abundance_plot(
  experiment = "20221129_EV1_136",
  sample = "plasma",
  condition = "basal",
  label_proteins = c("APOA1","C5","FIBG","CFH","LIFR","FA5","MBL2","TRFE","HEMO","MASP2","FA9","MUG2","FGL1","PLSL")
)
save_plot(
  fn = paste0("3e_abundance_plot_hepatocyte"),
  ht = 4,
  wd = 2
)

abundance_plot(
  experiment = "20221130_EV1_137",
  sample = "plasma",
  condition = "basal",
  label_proteins = c("LIFR","CPN2","LRP1","ADIPO","PLSL","CFD","TGFB1","TSP4")
)
save_plot(
  fn = paste0("3e_abundance_plot_adipocyte"),
  ht = 4,
  wd = 2
)

log2(47554.3)
```


## S3B: Correlation scatterplot

```{r, fig.width=4, fig.height=2}


abundance_scatterplot <- function(experiment, label_proteins, fig_num){
  df <- read_experiment(experiment, "serum") %>%
    add_alias()
  print(df %>% filter(alias == "LRP1"))
    # select ID and signal intensity columns
    df <- df %>% select(
      c(uniprot_id, alias, Outcyte, Mass),
      contains("basal") & contains("cre+")
    ) %>%
    mutate(Mass = as.numeric(Mass)) %>%
    select(-c(contains("cre-"))) %>%
    # take mean signal intensity
    pivot_longer(cols = -c(uniprot_id, alias, Outcyte, Mass)) %>%
    group_by(uniprot_id, alias, Outcyte, Mass) %>%
    summarise(mean_signal_intensity = mean(value)) %>%
    inner_join(published_data, by = "uniprot_id") %>%
    mutate(
      Outcyte = replace_na(Outcyte, "NA"),
      Outcyte = recode(Outcyte, !!!replace_list),
      Outcyte = factor(Outcyte, levels = rev(names(palette)))
    )
  print(cor(
    log2(df$published_concentration),
    log2(df$mean_signal_intensity)
  ))
  lbl_df <- df %>% filter(alias %in% label_proteins)
  print(df %>% filter(alias == "LRP1"))
  plt <-
    df %>% ggplot(aes(
      x = log2(mean_signal_intensity),
      y = log2(published_concentration),
      fill = Outcyte,
      size = Mass
    )) +
    geom_point(
      shape = 21,
      color = "black",
      stroke = LINE_WIDTH,
      alpha = 0.8
    ) +
    turboid_theme() +
    theme(aspect.ratio = 1) +
    scale_fill_manual(name = NULL, values = palette) +
    scale_size_continuous(range = c(0.5, 4)) +
    labs(
      x = expression("log"[2] * "(mean signal intensity) basal plasma"),
      y = expression("published plasma concentration log"[2] * "(pmol/mL)")
    ) +
    geom_text_repel(data = lbl_df, mapping = aes(label = alias), size = FONT_SIZE_MM, min.segment.length = 0, segment.size = LINE_WIDTH, box.padding = 1.5, max.overlaps = Inf)

  print(plt)
  save_plot(
    fn = paste0("s3",fig_num,"_correlation", experiment),
    ht = 2,
    wd = 4
  )
}

exps <- c("a"= "20221129_EV1_136", "b" = "20221130_EV1_137")

abundance_scatterplot(
  "20221129_EV1_136", label_proteins = c("APOA1","C5","CFH","FA5","MASP1","TRFE","FA9","ADIPO"), fig_num = "d"
)

abundance_scatterplot(
  "20221130_EV1_137", label_proteins = c("LRP1","ADIPO","CFD","TGFB1","TSP4"), fig_num = "c"
)
```

## 3G: Upset Plot

```{r, fig.height=2.5, fig.width=3}
library(patchwork)
library(ComplexUpset)
library(ggplot2)

sets <- list(
  `Hepatocyte serum` = read_experiment("20221129_EV1_136", "serum") %>% pull(uniprot_id),
  `Adipocyte serum` = read_experiment("20221130_EV1_137", "serum") %>% pull(uniprot_id),
  `Hepatocyte tissue` = read_experiment("20220714_EV1_98", "tissue") %>% pull(uniprot_id),
  `Adipocyte tissue` = read_experiment("20220807_EV1_101", "tissue") %>% pull(uniprot_id)
)

fasta_table <-
  "/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Mass-spectrometry-datasets/03_results/03_fasta_table_tp_fp/main_fasta_table_without_signal_p.csv" %>%
  read_csv() %>%
  select(uniprot_id, Outcyte, Mass)

# binary data frame
all_elements <- unique(unlist(sets))
df <- as.data.frame(sapply(sets, function(set) {
  all_elements %in% set
}))
df <- cbind(element = all_elements, df) %>%
  rename(c("uniprot_id" = "element")) %>%
  left_join(fasta_table, by = "uniprot_id") %>%
  mutate(Mass = as.numeric(Mass)) %>%
  mutate(
    Outcyte = replace_na(Outcyte, "NA"),
    Outcyte = recode(Outcyte, !!!replace_list),
    Outcyte = factor(Outcyte, levels = rev(names(palette)))
  )
upset_plot_theme <-
  theme_classic() +
  theme(
    axis.text.y = TEXT_ELEMENT,
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank(),
    axis.title.y = TEXT_ELEMENT,
    panel.grid = element_blank(),
    axis.line.x = AXIS_LINE,
    axis.line.y = AXIS_LINE
  )

upset(
  df,
  sort_sets = FALSE,
  intersect = names(sets),
  set_sizes = FALSE,
  matrix = (intersection_matrix(
    geom = geom_point(
      size = 1
    ),
    segment = geom_segment(
      linewidth = LINE_WIDTH
    )
  )),
  annotations = list(
    "intersection size" = intersection_size(
      counts = TRUE,
      #mapping = aes(fill = POINT_FILL),
      fill = POINT_FILL,
      color = "black",
      size = LINE_WIDTH,
      show.legend = FALSE,
      width = 0.7,
      text = list(size = FONT_SIZE_MM, color = "black", family = FONT_FAMILY, vjust = -0.1, check_overlap = TRUE)
    ) +
      scale_fill_manual(values = palette, name = NULL) +
      scale_y_continuous(expand = expansion(mult = c(0, 0.2)))
  ),
  base_annotations = list("% of proteins" = list(
    aes = aes(x = intersection, fill = Outcyte),
    geom = list(
      geom_bar(
        stat = "count",
        position = "fill",
        color = "black",
        size = LINE_WIDTH,
        show.legend = FALSE,
        width = 0.7
      ),
      scale_fill_manual(values = palette, name = NULL),
      scale_y_continuous(expand = expansion(mult = c(0, 0)), labels = scales::percent_format(accuracy = 1, suffix = ""), breaks = c(0, 0.5, 1))
    )
  )),
  stripes = "white",
  min_size = 10,
  themes = list(
    `% of proteins` = upset_plot_theme + theme(axis.ticks.y = AXIS_LINE),
    `intersection size` = upset_plot_theme + theme(axis.ticks.y = AXIS_LINE),
    intersections_matrix = upset_plot_theme + theme(axis.line.x = element_blank(), axis.line.y = element_blank(), axis.title.y = element_blank()),
    overall_sizes = upset_plot_theme + theme(axis.text.x = TEXT_ELEMENT, axis.title.y = element_blank(), axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks.x = AXIS_LINE)
  )
) + patchwork::plot_layout(heights = c(1, 0.4, 0.4))
save_plot("s3c_upset_plot", ht = 2.5, wd = 4)
```

```{r, fig.height=2.5, fig.width=4}
library(patchwork)
upset_plot_theme <-
  theme_classic() +
  theme(
    axis.text.y = TEXT_ELEMENT,
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank(),
    axis.title.y = TEXT_ELEMENT,
    panel.grid = element_blank(),
    axis.line.x = AXIS_LINE,
    axis.line.y = AXIS_LINE
  )

upset(
  df,
  sort_sets = FALSE,
  intersect = names(sets),
  set_sizes = FALSE, # (
  matrix = (intersection_matrix(
    geom = geom_point(
      size = 1
    ),
    segment = geom_segment(
      linewidth = LINE_WIDTH
    )
  )),
  base_annotations = list(
    "Intersection" = intersection_size(
      counts = TRUE,
      mapping = aes(fill = Outcyte),
      color = "black",
      size = LINE_WIDTH,
      show.legend = FALSE,
      width = 0.7,
      text = list(size = FONT_SIZE_MM, color = "black", family = FONT_FAMILY, vjust = -0.1, check_overlap = TRUE)
    ) +
      scale_fill_manual(values = palette, name = NULL) +
      scale_y_continuous(expand = expansion(mult = c(0, 0.2)))
  ),
  min_size = 10,
  stripes = "white",
  themes = list(
    `% of proteins` = upset_plot_theme + theme(axis.ticks.y = AXIS_LINE),
    `Intersection` = upset_plot_theme + theme(axis.ticks.y = AXIS_LINE),
    intersections_matrix = upset_plot_theme + theme(axis.line.x = element_blank(), axis.line.y = element_blank(), axis.title.y = element_blank()),
    overall_sizes = upset_plot_theme + theme(axis.text.x = TEXT_ELEMENT, axis.title.y = element_blank(), axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks.x = AXIS_LINE)
  )
) + patchwork::plot_layout(heights = c(1, 0.2))
save_plot("3g_upset_plot", ht = 2.5, wd = 4)
```

## 3F: dot plot

```{r, fig.height=3, fig.width=3.8}
fold_change_dot_plot <- function(highlight_genes) {
  df <- dep_path %>%
    read_csv(show_col_types = FALSE) %>%
    filter(comparison %in% c("LPS vs. basal", "fast vs. basal"))

  df <- df %>%
    mutate(`Entry Name` = entry_name) %>%
    add_alias() %>%
    filter(grepl("EV1_137|EV1_101|EV1_136|EV1_98", experiment)) %>%
    mutate(tissue = case_when(
      grepl("EV1_136|EV1_98", experiment) ~ "Hepatocyte",
      TRUE ~ "Adipocyte"
    )) %>%
    filter(alias %in% highlight_genes) %>%
    mutate(
      comparison = str_split(comparison, " vs. ") %>% map_chr(1),
      comparison = recode(comparison, !!!c("fast" = "Fasting")),
      alias = factor(alias, levels = rev(highlight_genes)),
      group = paste(tissue, sample_type),
      group = factor(
        group,
        levels = c(
          "Adipocyte tissue",
          "Hepatocyte tissue",
          "Adipocyte serum",
          "Hepatocyte serum"
        )
      )
    )
  print(nrow(df))
  plt <- df %>% 
    arrange(alias) %>%
    ggplot(aes(
    x = comparison,
    y = alias,
    fill = log2_FC,
    size = `-log10_pval`
  )) +
    geom_point(shape = 21, stroke = LINE_WIDTH) +
    facet_wrap(
      ~group,
      nrow = 1,
      labeller = label_wrap_gen(multi_line = FALSE),
      strip.position = "bottom"
    ) +
    turboid_theme() +
    theme(
      panel.spacing.x = unit(0, "mm"),
      panel.grid.major = element_line(color = "grey", linewidth = LINE_WIDTH),
      strip.placement = "outside",
      legend.position = "bottom",
      legend.key.height = unit(3, "mm"),
      legend.key.width = unit(4, "mm")
    ) +
    scale_fill_gradient2(
      high = "red",
      low = "blue",
      mid = "white",
      limits = c(-3, 3),
      oob = squish,
      name = expression("log"[2] * "(FC from basal)")
    ) +
    scale_size_continuous(
      range = c(1, 4),
      name = expression("log"[2] * "(p-value)")
    ) +
    labs(x = NULL, y = NULL)
  print(plt)
  save_plot("3f_dot_plot", ht = 3, wd = 3.8)
  return(df)
}

old_highlight_genes <- c("CHLE","LIFR","C6","APOA1","C3","HPT","LPL","SERPINA3N","PLTP","APOE","SPA3M","A1AT5","ENPP2","C1S1","CBPQ","PZP","LBP","APOA4","KLKB1","MBL2","CBG","THBG","GRN","IBP4","HEMO","SAA1","ITIH4","SAA2","FGL1","RETN")

new_highlight_genes <- c("A1AT5","C1S1","C6","BCHE","LIFR","MBL2","KLKB1","LPL","LBP","PZP","APOE","C3","HEMO","HP","SAA1","SERPINA3N","APOA4","SERPINA3M")
df <- fold_change_dot_plot(
  highlight_genes =new_highlight_genes
)

```

## S3E correlation plots

```{r}
s3_d_g <- c("G6PE")

s3_d <- c(s3_d_g, c('PTER', 'GPAT3', 'CDNF', 'SAA2', 'CNPY2', 'FBLN3', 'FAM20C', 'HEPH', 'SPRC', 'FKBP5', 'SERPINA3N', 'MATN2', 'PLIN4', 'GBP2', 'EST1', 'SAA1', 'MYADM', 'STEA4', 'TGFB1', 'NPC2', 'CES1D', 'SERPINA3C', 'THRSP', 'CP7A1'))

s3_e <- c(s3_d_g, c('SERPINA3C', 'PLIN1', 'PLIN4', 'CLC11', 'GAS6', 'TSP2', 'LDLR', 'AMPE', 'MYADM', 'SPRC', 'LIFR'))

s3_f <- c(s3_d_g, c('PLIN1', 'PLIN4', 'ANXA1', 'CDNF', 'ANGL2', 'ERLN1', 'NAMPT', 'SAA1', 'LDLR', 'PODN', 'HFE', 'CATD', 'PCSK6', 'AMPE', 'SPRC', 'ERLN2', 'NENF', 'SERPINA3N'))

s3_g <- c(s3_d_g, c('TSP2'))
```

```{r, fig.height=4, fig.width=2}
# hepatocyte
correlation_min <- -5
correlation_max <- 6.4


# liver vs plasma LPS stimulation
correlation_plot(
  timepoints = c(
    "x" = "20220714_EV1_98", # x is liver
    "y" = "20221129_EV1_136" # y is plasma
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "serum"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "liver 15w p < 0.05" = "#d6e5b3",
    "plasma 15w p < 0.05" = "#75c489",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#5d8f70"
  ),
  num_top = 5,
  x_lab = expression("liver, log"[2] * "(LPS/basal)"),
  y_lab = expression("plasma, log"[2] * "(LPS/basal)"),
  drop = "fast"#,
  #top = s3_d
)

save_plot(
  fn = "s3d",
  wd = 2,
  ht = 4
)

# liver vs plasma LPS stimulation
correlation_plot(
  timepoints = c(
    "x" = "20220714_EV1_98", # x is liver
    "y" = "20221129_EV1_136" # y is plasma
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "serum"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "liver 15w p < 0.05" = "#c4dfec",
    "plasma 15w p < 0.05" = "#85c6ed",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#4482c3"
  ),
  num_top = 5,
  x_lab = expression("liver, log"[2] * "(fast/basal)"),
  y_lab = expression("plasma, log"[2] * "(fast/basal)"),
  drop = "LPS"#,
  #top = s3_e
)

save_plot(
  fn = "s3e",
  wd = 2,
  ht = 4
)

# adipocyte

correlation_plot(
  timepoints = c(
    "x" = "20220807_EV1_101", # x is liver
    "y" = "20221130_EV1_137" # y is plasma
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "serum"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "iWAT 15w p < 0.05" = "#d6e5b3",
    "plasma 15w p < 0.05" = "#75c489",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#5d8f70"
  ),
  num_top = 5,
  x_lab = expression("iWAT, log"[2] * "(LPS/basal)"),
  y_lab = expression("plasma, log"[2] * "(LPS/basal)"),
  drop = "fast"#,
  #top = s3_f
)

save_plot(
  fn = "s3f",
  wd = 2,
  ht = 4
)

correlation_plot(
  timepoints = c(
    "x" = "20220807_EV1_101", # x is liver
    "y" = "20221130_EV1_137" # y is plasma
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "serum"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "iWAT 15w p < 0.05" = "#c4dfec",
    "plasma 15w p < 0.05" = "#85c6ed",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#4482c3"
  ),
  num_top = 5,
  x_lab = expression("iWAT, log"[2] * "(fast/basal)"),
  y_lab = expression("plasma, log"[2] * "(fast/basal)"),
  drop = "LPS"#,
  #top = s3_g
)

save_plot(
  fn = "s3g",
  wd = 2,
  ht = 4
)
```

# Figure 4

## S4I: Volcano plot

```{r}
# read mass spec data
# transform multiple pipeline outputs into a tidy dataframe
file_paths <- list(
  "iWAT" = "20240427_CRW_B17A",
  "eWAT" = "20240429_CRW_B17B"
)
df <- imap_dfr(file_paths, ~
  read_experiment(.x, sample_type = "tissue") %>%
    dplyr::rename(protein = `Entry Name`, gene = gene_name) %>%
    dplyr::select(protein, gene, contains("iWAT_HFD vs. iWAT_chow"), contains("eWAT_HFD vs. eWAT_chow")) %>%
    mutate(tissue = .y))

# tidy column names
for (col in c("Regulation", "-log10_pval", "log2_FC")) {
  for (comparison in c("iWAT_HFD vs. iWAT_chow", "eWAT_HFD vs. eWAT_chow")) {
    df <- df %>%
      mutate(!!paste0(col, ";", comparison) := coalesce(!!!dplyr::select(., contains(col) &
        contains(comparison))))
  }
}
print(df)

df <- df %>%
  dplyr::select(-ends_with(")")) %>%
  pivot_longer(
    cols = starts_with("Regulation") |
      starts_with("-log10_pval") | starts_with("log2_FC"),
    names_to = c(".value", "comparison"),
    names_sep = ";"
  ) %>%
  mutate(group = Regulation, log2FC = log2_FC, comparison = "HFD") %>%
  mutate(`Entry Name` = protein) %>%
  add_alias()

df
```

## S4J GO term

```{r, fig.width=1.5, fig.height=1.2}
facetted_go_term(
  file_paths = list(
    "iWAT" = "20240427_CRW_B17A",
    "eWAT" = "20240429_CRW_B17B"
  ),
  comparison_1 = "iWAT_HFD vs. iWAT_chow",
  comparison_2 = "eWAT_HFD vs. eWAT_chow",
  filter_direction = TRUE
)

save_plot(
  "s4j_go_term",
  ht = 1.2,
  wd = 1.5
)
```

## concat heatmap

```{r}
go_term_name <- "protein folding"
# gt <- get_study_genes(go_term_name)
# gt <- c("Fgb","Fgg","C3","C4b","Fga","Apoa1","C6","Stat1","Apcs","Apoa4","Tfrc","Pml","Hp","Rbp4")
# gt <- c("Itgb1","Col18a1","St3gal4","Sorbs3","Slc4a1","Itgb5","Fndc3b","Siglec1","Ptprd","Gpc4","Dmd","Tgm2","Afdn","Parva")
df2 <- read_experiment("20240427_CRW_B17A", "tissue") %>%
  filter(gene_name %in% gt) %>%
  prepare_fc_data("chow")
rownames(df2) <- paste("iWAT", rownames(df2))
df1 <- read_experiment("20240429_CRW_B17B", "tissue") %>%
  filter(gene_name %in% gt) %>%
  prepare_fc_data("chow")
rownames(df1) <- paste("eWAT", rownames(df1))
df2 <- df2[, colnames(df2)[colnames(df2) %in% colnames(df1)]]
df1 <- df1[, colnames(df2)]
mat <- rbind(df1, df2)

pdf(
  file = paste0(paste0("s4j_heatmap_", go_term_name, ".pdf")),
  width = 3,
  height = 1.8
)

mat %>% fc_heatmap(output_filename = "aa", labels = c("HFD"), group_colors = c("#faa41a"), control_name = "chow")

lbl_gp <- gpar(col = "black", fontsize = 6, rot = 0, fontfamily = FONT_FAMILY)
group_block_anno(c(1), "empty", gp = gpar(fill = "grey90", col = "white"), label = "iWAT", label_gp = lbl_gp)
group_block_anno(c(2), "empty", gp = gpar(fill = "grey90", col = "white"), label = "eWAT", label_gp = lbl_gp)
dev.off()
```

### heatamp

Make heatmaps of the fold change of protein folding proteins in iWAT and
eWAT in mice on HFD vs chow diet

```{r, fig.height=1, fig.width=3}
read_experiment("20240427_CRW_B17A", "tissue") %>%
  filter(gene_name %in% get_study_genes("protein folding")) %>%
  prepare_fc_data("chow", filter_to_sig = TRUE) %>%
  fc_heatmap(output_filename = "s4j_fc_heatmap_iWAT.pdf", width = 3, height = 1, control_name = "chow", group_colors = c("#faa41a"), labels = c("HFD iWAT"), n_cell_types = 1, col_name_rot = 90)

read_experiment("20240429_CRW_B17B", "tissue") %>%
  filter(gene_name %in% get_study_genes("protein folding")) %>%
  prepare_fc_data("chow", filter_to_sig = TRUE) %>%
  fc_heatmap(output_filename = "s4j_fc_heatmap_eWAT.pdf", width = 3, height = 1, control_name = "chow", group_colors = c("#faa41a"), labels = c("HFD eWAT"), n_cell_types = 1, col_name_rot = 90)
```

## S4J go term

```{r, fig.width=2.1, fig.height=2.6}
file_paths <- list("a" = "20240907_CRW_B25A", "a" = "20240909_CRW_B25B")

facetted_go_term(file_paths,
  comparison_1 = "iWAT_HFD vs. iWAT_chow",
  comparison_2 = "eWAT_HFD vs. eWAT_chow"
)

save_plot(
  "4j_go_term",
  ht = 2.6,
  wd = 2.1
)
df <- paste0(PIPELINE_RESULTS_PATH, "turboid_go_term_analysis_ref_list.csv") %>%
  read_csv(show_col_types = FALSE) %>%
  filter(
    # filter to relevant results
    experiment %in% file_paths
  )

unique(df$comparison)
```

## Heatmap

```{r, fig.width=2.5, fig.height=5.5}
read_experiment("20240427_CRW_B17A", "tissue") %>%
  filter(gene_name %in% get_study_genes("inflammatory response")) %>%
  fc_heatmap(output_filename = "6d_fc_heatmap.pdf", width = 2.2, height = 3.8, control_name = "chow", group_colors = c("#faa41a"))


read_experiment("20240909_CRW_B25B", "tissue") %>%
  filter(gene_name %in% get_study_genes("inflammatory response")) %>%
  fc_heatmap(output_filename = "6d_fc_heatmap.pdf", width = 2.2, height = 3.8, control_name = "iWAT", group_colors = c("#faa41a"))
```

## 4J Volcano plot

```{r, fig.height=4, fig.width=4.5}

highlight_proteins <- "reference_data/Volcano plot proteins to highlight - Sheet1.csv" %>%
  read_csv(show_col_types = FALSE) %>%
  mutate(key = paste(protein, tissue, comparison, sep = "_")) %>%
  pull(key)
# read mass spec data
# transform multiple pipeline outputs into a tidy dataframe
comparisons <- c("eWAT_HFD vs. eWAT_chow", "iWAT_HFD vs. iWAT_chow")
file_paths <- list("iWAT_HFD" = "20240907_CRW_B25A", "eWAT_HFD" = "20240909_CRW_B25B")
#file_paths <- list(
#  "iWAT_HFD" = "20240427_CRW_B17A",
#  "eWAT_HFD" = "20240429_CRW_B17B"
#)
df <- imap_dfr(file_paths, ~
  read_experiment(.x, sample_type = "tissue") %>%
    dplyr::select(`Entry Name`, gene_name, contains(comparisons[1]), contains(comparisons[2])) %>%
    mutate(tissue = .y))

# tidy column names
for (col in c("Regulation", "-log10_pval", "log2_FC")) {
  for (comparison in comparisons) {
    df <- df %>%
      mutate(!!paste0(col, ";", comparison) := coalesce(!!!dplyr::select(., contains(col) &
        contains(comparison))))
  }
}
print(unique(df$comparison))
df <- df %>%
  dplyr::select(-ends_with(")")) %>%
  pivot_longer(
    cols = starts_with("Regulation") |
      starts_with("-log10_pval") | starts_with("log2_FC"),
    names_to = c(".value", "comparison"),
    names_sep = ";"
  ) %>%
  mutate(group = Regulation, log2FC = log2_FC, comparison = case_when(comparison == "eWAT_HFD vs. iWAT_HFD" ~ "HFD", TRUE ~ "HFD")) %>%
  add_alias() %>%
  mutate(tissue = case_when(tissue %in% c("iWAT_HFD") ~ "iWAT", TRUE ~ "eWAT"))

print(unique(df$tissue))
print(unique(df$comparison))
# build a annotation dataframe iteratively
rows <- list()
for (comp in unique(df$comparison)) {
  for (mouse_tissue in unique(df$tissue)) {
    n_up <- df %>%
      filter(
        comparison == comp,
        tissue == mouse_tissue,
        Regulation == "Significant Up"
      ) %>%
      nrow()
    up_row <- data.frame(
      text = paste(n_up, "up \nin", mouse_tissue, comp, " "),
      x_pos = Inf,
      hjustvar = 1,
      proteins = n_up,
      tissue = mouse_tissue,
      comparison = comp
    )
    n_down <- df %>%
      filter(
        comparison == comp,
        tissue == mouse_tissue,
        Regulation == "Significant Down"
      ) %>%
      nrow()
    down_row <- data.frame(
      text = paste(" ", n_down, "down\n. in", mouse_tissue, comp),
      x_pos = -Inf,
      hjustvar = -0,
      proteins = n_down,
      tissue = mouse_tissue,
      comparison = comp
    )
    rows <- append(rows, list(up_row, down_row))
  }
}
annotation_df <- bind_rows(rows)

label_df <-
  df %>%
  mutate(key = paste(alias, tissue, comparison, sep = "_")) %>%
  filter(key %in% highlight_proteins, Regulation %in% c("Significant Up", "Significant Down"))
print(df)
print("APOA4" %in% label_df$alias)
print("APOA4" %in% df$alias)
x_lim <- max(abs(df$log2_FC), na.rm = TRUE)

df %>%
  mutate(Regulation = factor(Regulation, levels = names(REGULATION_COLORS)), tissue = factor(tissue, levels = c("eWAT", "iWAT"))) %>%
  arrange(Regulation) %>%
  volcano_plot_base(
    params = list(
      stroke = LINE_WIDTH,
      show_legend = FALSE,
      palette = REGULATION_COLORS, alpha_palette = ALPHA_PALETTE
    ),
    left_annotation = "",
    right_annotation = ""
  ) +
  geom_text(
    data = annotation_df,
    aes(
      x = x_pos,
      y = Inf,
      hjust = hjustvar,
      vjust = 1.25,
      label = text
    ),
    inherit.aes = FALSE,
    size = FONT_SIZE_MM,
    fontface = "italic",
    lineheight = 0.95
  ) +
  geom_text_repel(data = label_df %>% filter(log2_FC > 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = 5.5 * 0.352778, xlim = c(1.5, x_lim), nudge_x = 1, nudge_y = 1, segment.color = "grey70") +
  geom_text_repel(data = label_df %>% filter(log2_FC < 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = 5.5 * 0.352778, xlim = c(-x_lim, 1.5), nudge_x = -1, nudge_y = 1, segment.color = "grey70") +
  facet_grid(cols = vars(tissue), axes = "all", axis.labels = "all") +
  theme(strip.text.y = TEXT_ELEMENT) +
  scale_x_continuous(expand = expansion(mult = c(0, 0)), limits = c(-x_lim, x_lim)) +
  ylim(0, max(df$`-log10_pval`, na.rm = TRUE) + 1) +
  xlab(expression("log"[2] * "(fold-change)"))
#save_plot(fn = "5a_volcano_plots", ht = 4.5, wd = 4.5)

max(df$`-log10_pval`, na.rm = TRUE) + 2

save_plot(
  "4jk_volcano",
  wd = 4.5,
  ht = 4
)

dep_path %>%
  read_csv() %>%
  filter(uniprot_id == "O88495")
```


# Figure 5

## Volcano plot

```{r}
# read mass spec data
# transform multiple pipeline outputs into a tidy dataframe
file_paths <- list(
  "6W_chow" = "20240430_CRW_B17C",
  "6W_HFD" = "20240501_CRW_B17D",
  "15W_chow" = "20240911_CRW_B25C",
  "15W_HFD" = "20240915_CRW_B25D"
)
df <- imap_dfr(file_paths, ~
  read_experiment(.x, sample_type = "tissue") %>%
    dplyr::select(`Entry Name`, gene_name, contains("eWAT_HFD vs. iWAT_HFD"), contains("eWAT_chow vs. iWAT_chow")) %>%
    mutate(tissue = .y))

# tidy column names
for (col in c("Regulation", "-log10_pval", "log2_FC")) {
  for (comparison in c("eWAT_HFD vs. iWAT_HFD", "eWAT_chow vs. iWAT_chow")) {
    df <- df %>%
      mutate(!!paste0(col, ";", comparison) := coalesce(!!!dplyr::select(., contains(col) &
        contains(comparison))))
  }
}
print(unique(df$comparison))
df <- df %>%
  dplyr::select(-ends_with(")")) %>%
  pivot_longer(
    cols = starts_with("Regulation") |
      starts_with("-log10_pval") | starts_with("log2_FC"),
    names_to = c(".value", "comparison"),
    names_sep = ";"
  ) %>%
  mutate(group = Regulation, log2FC = log2_FC, comparison = case_when(comparison == "eWAT_HFD vs. iWAT_HFD" ~ "HFD", TRUE ~ "chow")) %>%
  add_alias() %>%
  mutate(tissue = case_when(tissue %in% c("6W_chow", "6W_HFD") ~ "6W", TRUE ~ "15W")) %>%
  mutate(tissue = factor(tissue, levels = rev(c("6W", "15W"))))

# build a annotation dataframe iteratively
rows <- list()
for (comp in unique(df$comparison)) {
  for (mouse_tissue in unique(df$tissue)) {
    n_up <- df %>%
      filter(
        comparison == comp,
        tissue == mouse_tissue,
        Regulation == "Significant Up"
      ) %>%
      nrow()
    up_row <- data.frame(
      text = paste(n_up, "upregulated \nin", mouse_tissue, comp, "eWAT", " "),
      x_pos = Inf,
      hjustvar = 1,
      proteins = n_up,
      tissue = mouse_tissue,
      comparison = comp
    )
    n_down <- df %>%
      filter(
        comparison == comp,
        tissue == mouse_tissue,
        Regulation == "Significant Down"
      ) %>%
      nrow()
    down_row <- data.frame(
      text = paste(" ", n_down, "downregulated\n. in", mouse_tissue, comp, "eWAT"),
      x_pos = -Inf,
      hjustvar = -0,
      proteins = n_down,
      tissue = mouse_tissue,
      comparison = comp
    )
    rows <- append(rows, list(up_row, down_row))
  }
}
annotation_df <- bind_rows(rows)

label_df <-
  df %>%
  mutate(key = paste(alias, tissue, comparison, sep = "_")) %>%
  filter(key %in% highlight_proteins, Regulation %in% c("Significant Up", "Significant Down"))
print(df)

x_lim <- max(abs(df$log2_FC))

df %>%
  mutate(Regulation = factor(Regulation, levels = names(REGULATION_COLORS))) %>%
  arrange(Regulation) %>%
  arrange(tissue) %>%
  volcano_plot_base(
    params = list(
      stroke = LINE_WIDTH,
      show_legend = FALSE,
      palette = REGULATION_COLORS, alpha_palette = ALPHA_PALETTE
    ),
    left_annotation = "",
    right_annotation = ""
  ) +
  geom_text(
    data = annotation_df,
    aes(
      x = x_pos,
      y = Inf,
      hjust = hjustvar,
      vjust = 1.25,
      label = text
    ),
    inherit.aes = FALSE,
    size = FONT_SIZE_MM,
    fontface = "italic",
    lineheight = 0.95
  ) +
  geom_text_repel(data = label_df %>% filter(log2_FC > 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = FONT_SIZE_MM, xlim = c(1.5, x_lim), nudge_x = 1, nudge_y = 1) +
  geom_text_repel(data = label_df %>% filter(log2_FC < 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = FONT_SIZE_MM, xlim = c(-x_lim, 1.5), nudge_x = -1, nudge_y = 1) +
  facet_grid(cols = vars(tissue), rows = vars(comparison), axes = "all", axis.labels = "all") +
  xlim(-x_lim, x_lim) +
  ylim(0, max(df$`-log10_pval`, na.rm = TRUE) + 1) +
  xlab(expression("log"[2] * "(fold-change)")) +
  theme(strip.text.y = TEXT_ELEMENT)
save_plot(fn = "5a_volcano_plots", ht = 4.5, wd = 4.5)

max(df$`-log10_pval`, na.rm = TRUE) + 2
```

## 5F: GO term enrichment

```{r, fig.width=2.1, fig.height=3.1}
facetted_go_term(
  file_paths = list(
    "6W" = "20240430_CRW_B17C",
    "6W" = "20240501_CRW_B17D",
    "15W" = "20240911_CRW_B25C",
    "15W" = "20240915_CRW_B25D"
  ),
  comparison_1 = "eWAT_HFD vs. iWAT_HFD",
  comparison_2 = "eWAT_chow vs. iWAT_chow",
  go_class = "biological_process"
)

save_plot(
  fn = "5b_go_term",
  wd = 2.6,
  ht = 3.1
)
```

```{r, fig.width=2.6, fig.height=7}
# build a annotation dataframe iteratively
rows <- list()
for (comp in unique(df$comparison)) {
  for (mouse_tissue in unique(df$tissue)) {
    print(mouse_tissue)
    # tissue_name = case_when(mouse_tissue == "Hepatocytes" ~ "liver", TRUE ~ "fat")
    n_up <- df %>%
      filter(
        comparison == comp,
        tissue == mouse_tissue,
        Regulation == "Significant Up"
      ) %>%
      nrow()
    up_row <- data.frame(
      text = paste(n_up, "upregulated \nin", comp, mouse_tissue, " "),
      x_pos = Inf,
      hjustvar = 1,
      proteins = n_up,
      tissue = mouse_tissue,
      comparison = comp
    )
    n_down <- df %>%
      filter(
        comparison == comp,
        tissue == mouse_tissue,
        Regulation == "Significant Down"
      ) %>%
      nrow()
    down_row <- data.frame(
      text = paste(" ", n_down, "downregulated\n. in", comp, mouse_tissue),
      x_pos = -Inf,
      hjustvar = -0,
      proteins = n_down,
      tissue = mouse_tissue,
      comparison = comp
    )
    rows <- append(rows, list(up_row, down_row))
  }
}
annotation_df <- bind_rows(rows)

label_df <-
  df %>%
  mutate(key = paste(alias, tissue, comparison, sep = "_")) %>%
  filter(key %in% highlight_proteins, Regulation %in% c("Significant Up", "Significant Down"))
print(df)

x_lim <- max(abs(df$log2_FC))

df %>%
  mutate(Regulation = factor(Regulation, levels = names(REGULATION_COLORS))) %>%
  arrange(Regulation) %>%
  volcano_plot_base(
    params = list(
      stroke = LINE_WIDTH,
      show_legend = FALSE,
      palette = REGULATION_COLORS, alpha_palette = ALPHA_PALETTE
    ),
    left_annotation = "",
    right_annotation = ""
  ) +
  geom_text(
    data = annotation_df,
    aes(
      x = x_pos,
      y = Inf,
      hjust = hjustvar,
      vjust = 1.25,
      label = text
    ),
    inherit.aes = FALSE,
    size = FONT_SIZE_MM,
    fontface = "italic",
    lineheight = 0.95
  ) +
  geom_text_repel(data = label_df %>% filter(log2_FC > 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = FONT_SIZE_MM, xlim = c(1.5, x_lim), nudge_x = 1, nudge_y = 1) +
  geom_text_repel(data = label_df %>% filter(log2_FC < 0), mapping = aes(label = alias), min.segment.length = 0, segment.size = LINE_WIDTH, max.overlaps = Inf, size = FONT_SIZE_MM, xlim = c(-x_lim, 1.5), nudge_x = -1, nudge_y = 1) +
  facet_grid(rows = vars(tissue), cols = vars(comparison), axes = "all", axis.labels = "all", scales = "free") +
  xlim(-x_lim, x_lim) +
  ylim(0, (max(df$`-log10_pval`, na.rm = TRUE) + 1)) +
  xlab(expression("log"[2] * "(fold-change)")) +
  theme(strip.text.y = TEXT_ELEMENT)
save_plot(fn = "4i_volcano_plots", ht = 7, wd = 2.6)
```

## 5G,H go-term correlation plot

```{r, fig.width=2.2635, fig.height=4}
get_study_genes <- function(go_term_name) {
  # helper method to pull a list of
  # genes related to a GO term
  study_genes <- go_path %>%
    read_csv(show_col_types = FALSE) %>%
    filter(term == go_term_name) %>%
    mutate(gene_list = str_extract_all(study_genes, "'[^']+'") %>%
      map(~ str_remove_all(.x, "'"))) %>%
    tidyr::unnest_longer(col = gene_list) %>%
    pull(gene_list) %>%
    unique()
  return(study_genes)
}

go_term_correlation <- function(file_paths, cell_type = "Hepatocytes", upper_limit = 6.4, lower_limit = -2.8, fn = "2i_correlation_plot", label_genes = c()) {
  # pull a list of immune process genes
  go_term_name_1 <- "immune system process"
  go_term_name_2 <- "cell adhesion"

  alpha_palette <- c(
    setNames(0.6, go_term_name_1),
    setNames(0.6, go_term_name_2),
    both = 0.7,
    other = 0.4
  )

  fill_palette <- c(
    setNames("#0D0887FF", go_term_name_2),
    setNames("#CC4678FF", go_term_name_1),
    both = "#edb180",
    other = "grey80"
  )

  color_palette <- c(
    setNames("#0D0887FF", go_term_name_2),
    setNames("#CC4678FF", go_term_name_1),
    both = "#edb180",
    other = "black"
  )

  study_genes_1 <- get_study_genes(go_term_name_1)
  study_genes_2 <- get_study_genes(go_term_name_2)

  # make a correlation plot

  dep_path %>%
    read_csv(show_col_types = FALSE) %>%
    filter(
      experiment %in% file_paths,
      comparison %in% c("eWAT_chow vs. iWAT_chow", "eWAT_HFD vs. iWAT_HFD")
    ) -> df
  print(unique(df$experiment))
  df %>%
    pivot_wider(
      id_cols = c(entry_name, gene_name),
      values_from = log2_FC,
      names_from = comparison
    ) %>%
    mutate(`Entry Name` = entry_name) %>%
    add_alias() %>%
    drop_na() %>%
    mutate(
      group =
        case_when(
          (gene_name %in% study_genes_1) & (gene_name %in% study_genes_2) ~ "both",
          (gene_name %in% study_genes_1) ~ go_term_name_1,
          (gene_name %in% study_genes_2) ~ go_term_name_2,
          TRUE ~ "other"
        )
    ) %>%
    arrange(desc(group)) -> df

  plt <- df %>%
    ggplot(aes(x = `eWAT_chow vs. iWAT_chow`, y = `eWAT_HFD vs. iWAT_HFD`, fill = group, alpha = group, color = group, label = alias)) +
    geom_vline(xintercept = 0, size = LINE_WIDTH, color = "grey90") +
    geom_hline(yintercept = 0, size = LINE_WIDTH, color = "grey90") +
    geom_segment(
      data = data.frame(),
      mapping = aes(
        x = c(lower_limit, lower_limit, lower_limit + 1),
        y = c(lower_limit + 1, lower_limit, lower_limit),
        xend = c(upper_limit - 1, upper_limit, upper_limit),
        yend = c(upper_limit, upper_limit, upper_limit - 1),
        linetype = c("dashed", "solid", "dashed")
      ),
      size = LINE_WIDTH,
      inherit.aes = FALSE,
      show.legend = FALSE
    ) +
    geom_point(
      data = df,
      shape = 21,
      size = 1.7,
      stroke = 0,
      color = "black",
      show.legend = TRUE
    ) +
    geom_text_repel(
      data = df %>% filter(alias %in% label_genes),
      size = FONT_SIZE_MM,
      show.legend = FALSE,
      # color = "black",
      alpha = 1,
      segment.size = LINE_WIDTH,
      min.segment.length = 0,
      family = FONT_FAMILY,
      max.overlaps = Inf,
    ) +
    turboid_theme() +
    ggtitle(paste0(
      gsub("s", "", cell_type),
      " HFD and chow\ntreatment correlation (",
      format(nrow(df), big.mark = ",", scientific = FALSE),
      " proteins)"
    )) +
    scale_fill_manual(
      values = fill_palette,
      name = NULL
    ) +
    scale_alpha_manual(
      values = alpha_palette,
      name = NULL
    ) +
    scale_color_manual(
      values = color_palette,
      name = NULL
    ) +
    guides(alpha = NULL, stroke = NULL, color = NULL, fill = guide_legend(nrow = 2)) +
    labs(
      x = expression("6w chow, log"[2] * "(eWAT/iWAT)"),
      y = expression("6w HFD, log"[2] * "(eWAT/iWAT)")
    ) +
    theme(legend.position = "top", legend.byrow = TRUE, aspect.ratio = 1, legend.margin = margin(b = -15), legend.key = element_blank()) +
    scale_x_continuous(expand = expansion(mult = c(0, 0)), limits = c(lower_limit, upper_limit)) +
    scale_y_continuous(expand = expansion(mult = c(0, 0)), limits = c(lower_limit, upper_limit)) +
    scale_linetype_manual(values = c("dashed" = "dashed", "solid" = "solid"))

  print(plt)

  save_plot(fn, wd = 2.2635, ht = 4)
  return(df)
}


go_term_correlation(file_paths = list(
  "chow" = "20240430_CRW_B17C",
  "HFD" = "20240501_CRW_B17D"
), cell_type = "chow", upper_limit = 5, lower_limit = -6, fn = "5g_correlation_plot", label_genes = c("C3", "C1QC", "C1QB", "C1QA", "VAV", "MYH4", "MPZ", "CO6A5", "CO6A1", "CO6A2", "HHATL", "MCSP", "MYH1", "DTX3L"))

go_term_correlation(file_paths = list("chow" = "20240911_CRW_B25C", "HFD" = "20240915_CRW_B25D"), cell_type = "chow", upper_limit = 5, lower_limit = -6, fn = "5h_correlation_plot", label_genes = c("C3", "C1QC", "C1QB", "C1QA", "VAV", "MYH4", "MPZ", "CO6A5", "CO6A1", "CO6A2", "HHATL", "MCSP", "MYH1", "DTX3L"))
```

## 5x correlation plot

```{r, fig.height=4, fig.width=2}


new_interdepot <- c("ANGPTL1",  "C1QA", "C1QB", "C1QC", "CATD", "HP", "PGDH", "THBS1","ADRB3" )


iwat_hfd_6w <- "#f7941d"
ewat_hfd_6w <- "#fede27"
iwat_hfd_15w <- "#ef4136"
ewat_hfd_15w <- "#9f1e37"
both <- "#7E614899"

number_proteins_to_label <- 5

correlation_plot(
  timepoints = c(
    "x" = "20240427_CRW_B17A",
    "y" = "20240907_CRW_B25A"
  ),
  min = -8,
  max = 5.5,
  sample_type = c("x" = "tissue", "y" = "tissue"),
  num_top = number_proteins_to_label,
  correlation_palette = c(
    "iWAT 6w p < 0.05" = iwat_hfd_6w,
    "iWAT 15w p < 0.05" = iwat_hfd_15w,
    "Not significant" = not_significant,
    "Both p < 0.05" = both
  ),
  x_lab = expression("iWAT 6w, log"[2] * "(HFD/chow)"),
  y_lab = expression("iWAT 15w, log"[2] * "(HFD/chow)"),
  drop = "blank",
  top = c(c('PPIC', 'NENF', 'PLIN1', 'MANF', 'LPL', 'LEP', 'CFD', 'SERPINF1', 'SYUG', 'FAM20C', 'PLIN4', 'APOA4', 'CDNF', 'G6PE', 'PLTP', 'APOE', 'LDLR', 'PAM'), new_interdepot)
)
save_plot("5d_correlation_plot",
  wd = 2,
  ht = 4
)
```

```{r, fig.height=4, fig.width=2}
correlation_plot(
  timepoints = c(
    "x" = "20240429_CRW_B17B",
    "y" = "20240909_CRW_B25B"
  ),
  min = -8,
  max = 5.5,
  sample_type = c("x" = "tissue", "y" = "tissue"),
  num_top = number_proteins_to_label,
  correlation_palette = c(
    "eWAT 6w p < 0.05" = ewat_hfd_6w,
    "eWAT 15w p < 0.05" = ewat_hfd_15w,
    "Not significant" = not_significant,
    "Both p < 0.05" = both
  ),
  x_lab = expression("eWAT 6w, log"[2] * "(HFD/chow)"),
  y_lab = expression("eWAT 15w, log"[2] * "(HFD/chow)"),
  drop = "blank",
  top = c(c('MANF', 'GPR50', 'LEP', 'FABP4', 'SYUG', 'PLIN1', 'FAM20C', 'PLTP', 'SERPINF1', 'PAM', 'PPIC', 'FSTL1', 'PLIN2', 'CFD', 'PLIN4', 'CDNF', 'G6PE', 'APOE', 'LPL', 'BHMT1', 'APOC3', 'APOA4', 'NENF'), new_interdepot)

)
save_plot("5e_correlation_plot",
  wd = 2,
  ht = 4
)

```

```{r, fig.height=4, fig.width=2}

depot_diff_proteins <- c("NPC2","SMOC1","SGPL1","CAVIN2","GPAT3","PRELP","CD1D1","TAP2","H2-D1","H2-K1")

correlation_plot(
  timepoints = c(
    "x" = "20240907_CRW_B25A",
    "y" = "20240909_CRW_B25B"
  ),
  min = -8,
  max = 5.5,
  sample_type = c("x" = "tissue", "y" = "tissue"),
  num_top = number_proteins_to_label,
  correlation_palette = c(
    "iWAT 15w p < 0.05" = iwat_hfd_15w,
    "eWAT 15w p < 0.05" = ewat_hfd_15w,
    "Not significant" = not_significant,
    "Both p < 0.05" = both
  ),
  x_lab = expression("iWAT 15w, log"[2] * "(HFD/chow)"),
  y_lab = expression("eWAT 15w, log"[2] * "(HFD/chow)"),
  top = c(c('MANF', 'GPR50', 'LEP', 'FABP4', 'SYUG', 'PLIN1', 'FAM20C', 'PLTP', 'SERPINF1', 'PAM', 'PLIN4', 'CDNF', 'G6PE', 'APOE', 'APOA4', 'NENF'), depot_diff_proteins),
  drop = "blank"
)
save_plot("5c_correlation_plot",
  wd = 2,
  ht = 4
)
```

```{r, fig.height=4, fig.width=2}
correlation_plot(
  timepoints = c(
    "x" = "20240427_CRW_B17A",
    "y" = "20240429_CRW_B17B"
  ),
  min = -8,
  max = 5.5,
  sample_type = c("x" = "tissue", "y" = "tissue"),
  num_top = number_proteins_to_label,
  correlation_palette = c(
    "iWAT 6w p < 0.05" = iwat_hfd_6w,
    "eWAT 6w p < 0.05" = ewat_hfd_6w,
    "Not significant" = not_significant,
    "Both p < 0.05" = both
  ),
  x_lab = expression("iWAT 6w, log"[2] * "(HFD/chow)"),
  y_lab = expression("eWAT 6w, log"[2] * "(HFD/chow)"),
  drop = "blank",
  top = c(c('MANF', 'GPR50', 'LEP', 'FABP4', 'SYUG', 'PLIN1', 'FAM20C', 'PLTP', 'SERPINF1', 'PAM', 'PLIN4',  'G6PE', 'APOE', 'APOA4', 'NENF'), depot_diff_proteins)
)
save_plot("5b_correlation_plot",
  wd = 2,
  ht = 4
)
```

## 5i ER heatmap

```{r, fig.width=3.8, fig.height=1}
endo_stress <- c("Abca7", "Abl1", "Aff4", "Afg2b", "Agr2", "Aifm1", "Akt1", "Akt2", "Akt3", "Alox15", "Alox5", "Amfr", "Anks4b", "Ankzf1", "Apaf1", "App", "Aqp11", "Asb11", "Atad3a", "Atf3", "Atf4", "Atf6", "Atf6b", "Atg10", "Atp2a1", "Atp2a3", "Atxn3", "Aup1", "Bag6", "Bak1", "Bax", "Bbc3", "Bbs1", "Bbs10", "Bcap31", "Bcl2", "Bcl2l1", "Bcl2l11", "Bfar", "Bhlha15", "Bid", "Bok", "Brsk2", "Calr", "Calr3", "Calr4", "Canx", "Casp12", "Casp3", "Casp9", "Cav1", "Ccdc47", "Ccnd1", "Cdk5rap3", "Cebpb", "Cep290", "Cert1", "Cftr", "Chac1", "Clgn", "Clu", "Cops5", "Creb3", "Creb3l1", "Creb3l2", "Creb3l3", "Crebrf", "D1Pas1", "Dab2ip", "Ddit3", "Ddrgk1", "Ddx3x", "Derl1", "Derl2", "Derl3", "Dnajb12", "Dnajb2", "Dnajb9", "Dnajc10", "Dnajc3", "Dnm1l", "Ecpas", "Edem1", "Edem2", "Edem3", "Eif2a", "Eif2ak2", "Eif2ak3", "Eif2ak4", "Eif2b5", "Eif2s1", "Eif4g1", "Elavl4", "Erlec1", "Erlin1", "Erlin2", "Ermp1", "Ern1", "Ern2", "Ero1a", "Erp27", "Erp29", "Erp44", "Faf1", "Faf2", "Fbxo17", "Fbxo2", "Fbxo27", "Fbxo44", "Fbxo6", "Fcgr2b", "Ficd", "Fis1", "Flot1", "Foxred2", "Get4", "Gorasp2", "Grina", "Gsk3b", "H13", "Herpud1", "Herpud2", "Hsp90b1", "Hspa5", "Hyou1", "Ifng", "Igtp", "Ikbkg", "Ins2", "Itpr1", "Jagn1", "Jkamp", "Jun", "Kcnj8", "Lhx1os", "Lpcat3", "Lrrk2", "Man1a", "Man1a2", "Man1b1", "Man1c1", "Manf", "Map3k20", "Map3k5", "Marchf6", "Marcks", "Mbtps2", "Nccrp1", "Nck1", "Nck2", "Nfe2l1", "Nfe2l2", "Nhlrc1", "Niban1", "Nod1", "Nod2", "Nploc4", "Nr1h2", "Nr1h3", "Nrbf2", "Nrros", "Nupr1", "Opa1", "Os9", "P4hb", "Park7", "Parp16", "Parp6", "Parp8", "Pdia2", "Pdia3", "Pdia4", "Pdia6", "Pdx1", "Pigbos1", "Pik3r1", "Pik3r2", "Pla2g6", "Pmaip1", "Pml", "Pmp22", "Ppp1r15a", "Ppp1r15b", "Ppp2cb", "Prkn", "Psmc6", "Ptpn1", "Ptpn2", "Qrich1", "Rasgrf1", "Rasgrf2", "Rcn3", "Rhbdd1", "Rnf103", "Rnf121", "Rnf139", "Rnf145", "Rnf183", "Rnf185", "Rnf186", "Rnf5", "Rnft1", "Rnft2", "Rpap2", "Scamp5", "Sdf2l1", "Sec16a", "Sec61b", "Sec61bl", "Sel1l", "Sel1l2", "Selenok", "Selenon", "Selenos", "Serinc3", "Serp1", "Serp2", "Sesn2", "Sgf29", "Sgta", "Sirt1", "Spop", "Srpx", "Stc2", "Stt3b", "Stub1", "Svip", "Syvn1", "Tardbp", "Tbl2", "Thbs1", "Thbs4", "Tmbim4", "Tmbim6", "Tmco1", "Tmed2", "Tmem117", "Tmem129", "Tmem238l", "Tmem258", "Tmem259", "Tmem33", "Tmem67", "Tmtc3", "Tmtc4", "Tmub1", "Tmub2", "Tmx1", "Tnfrsf10b", "Tor1a", "Trib3", "Trim13", "Trim25", "Trp53", "Txndc12", "Uba5", "Ubac2", "Ube2g2", "Ube2j1", "Ube2j2", "Ube2k", "Ube4a", "Ube4b", "Ubqln1", "Ubqln2", "Ubxn1", "Ubxn10", "Ubxn2a", "Ubxn4", "Ubxn6", "Ubxn8", "Ufc1", "Ufd1", "Ufl1", "Ufm1", "Umod", "Usp13", "Usp14", "Usp19", "Usp25", "Vapb", "Vcp", "Wfs1", "Xbp1", "Yod1")

read_experiment("20240907_CRW_B25A", "tissue") %>%
  filter(gene_name %in% endo_stress) %>%
  prepare_fc_data("chow", filter_to_sig = TRUE) %>%
  fc_heatmap(output_filename = "5i_fc_heatmap_iWAT.pdf", width = 3.8, height = 1, control_name = "chow", group_colors = c(iwat_hfd_15w), labels = c("15w HFD iWAT"), n_cell_types = 1, col_name_rot = 90)

read_experiment("20240909_CRW_B25B", "tissue") %>%
  filter(gene_name %in% endo_stress) %>%
  prepare_fc_data("chow", filter_to_sig = TRUE) %>%
  fc_heatmap(output_filename = "5i_fc_heatmap_eWAT.pdf", width = 3.8, height = 1, control_name = "chow", group_colors = c(ewat_hfd_15w), labels = c("15w HFD eWAT"), n_cell_types = 1, col_name_rot = 90)
```

# Figure 6

```{r}
# check number quantified in each experiment
for (experiment in c(
  "6w" = "20240401_CRW_B13",
  "15w" = "20240917_CRW_B30"
)) {
  experiment %>%
    read_experiment(sample_type = "serum") %>%
    pull(uniprot_id) %>%
    unique() %>%
    length() %>%
    print()
}
```

## 6D: Heatmap

```{r, fig.width=2.06, fig.height=3.3}
read_experiment("20240401_CRW_B13", "plasma") %>%
  fc_heatmap_with_annotation(
    output_filename = "6d_fc_heatmap_6w.pdf",
    width = 2.06,
    height = 3.3,
    control_name = "chow",
    group_colors = c("#faa41a")
  )
```

## 6E: Heatmap

```{r, fig.width=2.2, fig.height=5.7}
read_experiment("20240917_CRW_B30", "plasma") %>%
  fc_heatmap_with_annotation(
    output_filename = "6e_fc_heatmap_15w.pdf",
    width = 2.2,
    height = 5.7,
    control_name = "chow",
    group_colors = c("#ed2024")
  )
```

## 6G: Molecular weight bar plot

```{r, fig.height=1.1, fig.width=1.9723}
# 6W HFD
w6 <- read_experiment("20240401_CRW_B13", "plasma") %>%
  dplyr::select(uniprot_id, Mass) %>%
  mutate(timepoint = "plasma 6W")
# 15W HFD
mw_df <- read_experiment("20240917_CRW_B30", "plasma") %>%
  dplyr::select(uniprot_id, Mass) %>%
  mutate(timepoint = "plasma 15W") %>%
  rbind(w6)

mw_df <- read_experiment("20240909_CRW_B25B", "tissue") %>%
  dplyr::select(uniprot_id, Mass) %>%
  mutate(timepoint = "tissue 6W") %>%
  rbind(mw_df)

mw_df <- read_experiment("20240907_CRW_B25A", "tissue") %>%
  dplyr::select(uniprot_id, Mass) %>%
  mutate(timepoint = "tissue 15W") %>%
  rbind(mw_df)

mw_palette <- c(
  ">60 kDa" = "#999b9e",
  "30-60 kDa" = "#841E5AFF",
  "15-30 kDa" = "#F06043FF",
  "<15 kDa" = "#FAEBDDFF"
)

# bin data
gg_obj <- mw_df %>%
  mutate(
    Mass = Mass / 1000, # convert to kDa
    binned_mass = case_when(
      Mass > 60 ~ ">60 kDa",
      Mass > 30 ~ "30-60 kDa",
      Mass > 15 ~ "15-30 kDa",
      TRUE ~ "<15 kDa",
    )
  ) %>%
  mutate(binned_mass = factor(binned_mass, levels = rev(names(mw_palette)))) %>%
  arrange(binned_mass) %>%
  ggplot(aes(
    y = timepoint,
    fill = binned_mass
  )) +
  geom_bar(position = "fill", size = LINE_WIDTH, color = "black", width = 0.65) +
  scale_fill_manual(values = mw_palette)
percent_barplot_theme(gg_obj)
save_plot("6g_molecular_weight", ht = 1.1, wd = 1.9723)
```

### Molecular weight boxplot

```{r, fig.width=2, fig.height=1.5}
mw_df %>%
  ggplot(aes(x = log2(Mass / 1000), y = timepoint)) +
  geom_boxplot(size = LINE_WIDTH, outlier.size = 0.5) +
  turboid_theme() +
  labs(y = NULL, x = expression("log"[2] * "(kDA molecular weight)"))

save_plot("s6_boxplot", wd = 2, ht = 1.5)

mw_df %>%
  arrange(desc(Mass)) %>%
  head()
```

## 6H: Outcyte percent barplot

```{r, fig.height=1.1, fig.width=2.2}
replace_list <- c(
  "Intracellular" = "Intracellular",
  "Signal_Peptide" = "Signal Peptide",
  "Transmembrane" = "Transmembrane",
  "UPS" = "UPS",
  "NA" = "Other"
)
palette <- c(
  "Signal Peptide" = "#721f81",
  "Intracellular" = "#b73779",
  "UPS" = "#f1605d",
  "Transmembrane" = "#feb078",
  "Other" = "lightgrey"
)

alb_plasma <- read_experiment("20240401_CRW_B13", "serum") %>%
  dplyr::select(uniprot_id, Outcyte) %>%
  mutate(experiment = "plasma 6W")
outcyte_df <- read_experiment("20240917_CRW_B30", "serum") %>%
  dplyr::select(uniprot_id, Outcyte) %>%
  mutate(experiment = "plasma 15W") %>%
  rbind(alb_plasma)

outycte_barplot(outcyte_df)
save_plot("6c_percent_barplot", ht = 1.1, wd = 2.2)

outcyte_df <- read_experiment("20240909_CRW_B25B", "tissue") %>%
  dplyr::select(uniprot_id, Outcyte) %>%
  mutate(experiment = "iWAT tissue 6W") %>%
  rbind(outcyte_df)

outcyte_df <- read_experiment("20240907_CRW_B25A", "tissue") %>%
  dplyr::select(uniprot_id, Outcyte) %>%
  mutate(experiment = "iWAT tissue 15W") %>%
  rbind(outcyte_df)

outycte_barplot(outcyte_df)


outcyte_df

save_plot("s6a_percent_barplot", ht = 1.1, wd = 2.2)
```

## 6F: correlation scatter

```{r, fig.width=4, fig.height=2}
s6_scatterplot_list <- c('LBP', 'LEP', 'CES1D', 'SERPINA3C', 'SYUG', 'CNPY2', 'C6', 'PLIN1', 'FAM20C', 'PLTP', 'SERPINF1', 'PAM', 'PPIC', 'FSTL1', 'CFD', 'PLIN4', 'G6PE', 'APOE', 'LPL', 'APOC3', 'C3', 'APOA4', 'NENF', 'LRG1')

correlation_plot(
  timepoints = c(
    "x" = "20240401_CRW_B13",
    "y" = "20240917_CRW_B30"
  ),
  sample_type = c("x" = "serum", "y" = "serum"),
  min = -3.2,
  max = 4,
  correlation_palette = c(
    "6W p < 0.05" = "orange",
    "15W p < 0.05" = "red",
    "Not significant" = "grey",
    "Both p < 0.05" = "darkred"
  ),
  x_lab = expression("plasma 6w, log"[2] * "(HFD/chow)"),
  y_lab = expression("plasma 15w, log"[2] * "(HFD/chow)"),
  drop=  "blank",
  top = s6_scatterplot_list
)

save_plot("6f_correlation_plot",
  wd = 4,
  ht = 2
)
```

```{r, fig.width=4, fig.height=2}
```

### Plasma vs tissue


```{r, fig.width=4, fig.height=2}
correlation_plot(
  timepoints = c(
    "x" = "20240917_CRW_B30",
    "y" = "20240907_CRW_B25A"
  ),
  min = -7.6,
  max = 5,
  sample_type = c("x" = "serum", "y" = "tissue"),
  num_top = 10,
  x_lab = expression("plasma 15w, log"[2] * "(HFD/chow)"),
  y_lab = expression("iWAT tissue 15w, log"[2] * "(HFD/chow)"),
  correlation_palette = c(
    "Plasma p < 0.05" = "orange",
    "Tissue p < 0.05" = "red",
    "Not significant" = "grey",
    "Both p < 0.05" = "darkred"
  ),
  drop = "blank",
  top = s6_scatterplot_list
)
save_plot("6g_correlation_plot",
  wd = 4,
  ht = 2
)


correlation_plot(
  timepoints = c(
    "x" = "20240917_CRW_B30",
    "y" = "20240909_CRW_B25B"
  ),
  min = -7.6,
  max = 5,
  sample_type = c("x" = "serum", "y" = "tissue"),
  num_top = 10,
  x_lab = expression("plasma 15w, log"[2] * "(HFD/chow)"),
  y_lab = expression("eWAT tissue 15w, log"[2] * "(HFD/chow)"),
  correlation_palette = c(
    "Plasma p < 0.05" = "orange",
    "Tissue p < 0.05" = "red",
    "Not significant" = "grey",
    "Both p < 0.05" = "darkred"
  ),
  drop = "blank",
  top = s6_scatterplot_list
)
save_plot("s6b_correlation_plot",
  wd = 4,
  ht = 2
)
```

## 6I Abundance plot

comparing abundance in HFD plasma dat to published concentrations

```{r, fig.width=2, fig.height=4}
abundance_plot_highlights_6 <- c("SYUG", "LRG1", "G6PE", "CFD", "PAM", "APOA4", "SERPINF1", "LEP")
for (experiment in c(
  "6w" = "20240401_CRW_B13",
  "15w" = "20240917_CRW_B30"
)) { # 6w and 15w
  abundance_plot(
    experiment = experiment,
    sample_type = serum,
    condition = "HFD",
    label_proteins = abundance_plot_highlights_6
  )
  save_plot(
    fn = paste0("6i_abundance_plot", experiment),
    ht = 4,
    wd = 2
  )
}

envinfo
```

# Figure 7

## 7C Bubble plot

```{r, fig.height=5.5, fig.width=3.9}
bubble_plot <- function(proteins, chapters) {
  df <-
    "/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Reference datasets/UKBB_plasma_proteome_atlas/ukbb_turboid_intersect_all_associations.csv" %>%
    read_csv(
      show_col_types = FALSE,
      col_types = cols(P_value = col_character())
    ) %>%
    mutate(
      P_value = as.numeric(P_value),
    ) %>%
    filter(
      toupper(Protein) %in% toupper(proteins),
      Disease_category %in% chapters,
      disease_type == "prevalent"
    )

  sig_diseases <- df %>%
    filter(`significant_boneferroni_p-value_less_than_0.05` == TRUE) %>%
    pull(Disease) %>%
    unique()

  plt <- df %>%
    filter(Disease %in% sig_diseases) %>%
    mutate(
      `HR_or_OR[95%CI]` = str_split(`HR_or_OR[95%CI]`, " ") %>% map_chr(1) %>% as.numeric(),
      Disease_category = gsub("Chapter [IVX]+ ", "", Disease_category) %>% str_wrap(width = 25),
      Disease = str_wrap(Disease, width = 40),
      Protein = factor(Protein, levels = proteins)
    ) %>%
    ggplot(aes(
      x = Protein,
      y = reorder_within(Disease, by = -log2(P_value), within = Disease_category),
      size = -log10(P_value),
      fill = log2(`HR_or_OR[95%CI]`)
    )) +
    geom_point(
      shape = 21,
      color = "black",
      stroke = LINE_WIDTH
    ) +
    facet_grid(
      rows = vars(Disease_category),
      scales = "free",
      space = "free"
    ) +
    turboid_theme() +
    theme(panel.grid.major = element_line(color = "grey90", linewidth = LINE_WIDTH)) +
    scale_fill_gradient2(
      high = "red",
      low = "blue",
      mid = "white",
      limits = c(-2.3, 2.3),
      midpoint = 0,
      na.value = "red"
    ) +
    scale_size_continuous(range = c(0.5, 3.8), breaks = c(20, 40, 60)) +
    theme(
      strip.text = element_text(
        size = FONT_SIZE,
        color = "black",
        family = FONT_FAMILY
      ),
      axis.text.x = element_text(
        size = FONT_SIZE,
        color = "black",
        family = FONT_FAMILY,
        angle = 45,
        vjust = 1,
        hjust = 1
      ),
      legend.spacing.y = unit(5, "mm"),
      legend.position = "right",
      legend.justification = "center"
    ) +
    labs(
      x = NULL,
      y = NULL,
      fill = expression("log"[2] * "(association)"),
      size = expression("-log"[10] * "(p-value)")
    ) +
    guides(fill = guide_colorbar(
      barwidth = 0.6,
      barheight = 4,
    )) +
    scale_y_reordered()
  print(plt)
  return(plt)
}

bubble_plot(
  proteins = c("LEP","SNCG","CFD","LRG1","APOA4","PAM","SERPINF1","BCHE","GSN","GHR"),
  chapters = c(
    "Chapter IV Endocrine, nutritional and metabolic diseases",
    "Chapter IX Diseases of the circulatory system"
  )
)

save_plot <- function(fn, wd, ht) {
  ggsave(
    paste0(PLOT_RESULTS_PATH, fn, ".pdf"),
    width = wd,
    height = ht,
    dpi = 300,
    device = cairo_pdf
  )
}

save_plot(
  fn = "7c_dot_plot_circulatory_endocrine",
  wd = 3.9,
  ht = 5.5
)



```


```{r, fig.height=5.5, fig.width=3.9}
proteins_1 = c("LEP","SNCG","CFD","LRG1","APOA4","PAM","SERPINF1","BCHE","GSN","GHR")
proteins_2 = c("APOA4","SERPINF1","BCHE","LIFR","ITIH3","C7","FGL1","AMBP","GSN","GHR")
chapters_1 = c(
  "Chapter IV Endocrine, nutritional and metabolic diseases",
  "Chapter IX Diseases of the circulatory system"
)
chapters_2 = c(
  "Chapter I Certain infectious and parasitic diseases"
)

df <-
  "/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Reference datasets/UKBB_plasma_proteome_atlas/ukbb_turboid_intersect_all_associations.csv" %>%
  read_csv(
    show_col_types = FALSE,
    col_types = cols(P_value = col_character())
  ) %>%
  mutate(
    P_value = as.numeric(P_value),
  ) %>%
  filter(
    (toupper(Protein) %in% toupper(proteins_1)) & (Disease_category  %in% chapters_1) |
    (toupper(Protein) %in% toupper(proteins_2)) & (Disease_category  %in% chapters_2),
    disease_type == "prevalent"
  )

sig_diseases <- df %>%
  filter(`significant_boneferroni_p-value_less_than_0.05` == TRUE) %>%
  pull(Disease) %>%
  unique()

plt <- df %>%
  filter(Disease %in% sig_diseases) %>%
  mutate(
    `HR_or_OR[95%CI]` = str_split(`HR_or_OR[95%CI]`, " ") %>% map_chr(1) %>% as.numeric(),
    Disease_category = gsub("Chapter [IVX]+ ", "", Disease_category) %>% str_wrap(width = 25),
    Disease = str_wrap(Disease, width = 40),
    Protein = factor(Protein, levels = unique(c(proteins_1, proteins_2)))
  ) %>%
  ggplot(aes(
    x = Protein,
    y = reorder_within(Disease, by = -log2(P_value), within = Disease_category),
    size = -log10(P_value),
    fill = log2(`HR_or_OR[95%CI]`)
  )) +
  geom_point(
    shape = 21,
    color = "black",
    stroke = LINE_WIDTH
  ) +
  facet_grid(
    rows = vars(Disease_category),
    scales = "free",
    space = "free"
  ) +
  turboid_theme() +
  theme(panel.grid.major = element_line(color = "grey90", linewidth = LINE_WIDTH)) +
  scale_fill_gradient2(
    high = "red",
    low = "blue",
    mid = "white",
    limits = c(-2.3, 2.3),
    midpoint = 0,
    na.value = "red"
  ) +
  scale_size_continuous(range = c(0.5, 3.8), breaks = c(20, 40, 60)) +
  theme(
    strip.text = element_text(
      size = FONT_SIZE,
      color = "black",
      family = FONT_FAMILY
    ),
    axis.text.x = element_text(
      size = FONT_SIZE,
      color = "black",
      family = FONT_FAMILY,
      angle = 45,
      vjust = 1,
      hjust = 1
    ),
    legend.spacing.y = unit(5, "mm"),
    legend.position = "right",
    legend.justification = "center"
  ) +
  labs(
    x = NULL,
    y = NULL,
    fill = expression("log"[2] * "(association)"),
    size = expression("-log"[10] * "(p-value)")
  ) +
  guides(fill = guide_colorbar(
    barwidth = 0.6,
    barheight = 4,
  )) +
  scale_y_reordered()
print(plt)



save_plot <- function(fn, wd, ht) {
ggsave(
  paste0(PLOT_RESULTS_PATH, fn, ".pdf"),
  width = wd,
  height = ht,
  dpi = 300,
  device = cairo_pdf
)
}

save_plot(
fn = "7c_dot_plot_circulatory_endocrine",
wd = 3.9,
ht = 5.5
)



```


```{r, fig.width=6, fig.height=5.2}
library(patchwork)

proteins_1 = c("LEP","SNCG","CFD","LRG1","APOA4","PAM","SERPINF1","BCHE","GSN","GHR")
proteins_2 = c("APOA4","SERPINF1","BCHE","LIFR","ITIH3","C7","FGL1","AMBP","GSN","GHR")
chapters_1 = c(
  "Chapter IV Endocrine, nutritional and metabolic diseases",
  "Chapter IX Diseases of the circulatory system"
)
chapters_2 = c(
  "Chapter I Certain infectious and parasitic diseases"
)

df <-
  "/Users/henrysanford/Dropbox @RU Dropbox/Vinogradova Laboratory/TurboID manuscript/Reference datasets/UKBB_plasma_proteome_atlas/ukbb_turboid_intersect_all_associations.csv" %>%
  read_csv(
    show_col_types = FALSE,
    col_types = cols(P_value = col_character())
  ) %>%
  mutate(
    P_value = as.numeric(P_value),
  ) %>%
  filter(
    (toupper(Protein) %in% toupper(proteins_1)) & (Disease_category  %in% chapters_1) |
    (toupper(Protein) %in% toupper(proteins_2)) & (Disease_category  %in% chapters_2),
    disease_type == "prevalent"
  )

sig_diseases <- df %>%
  filter(`significant_boneferroni_p-value_less_than_0.05` == TRUE) %>%
  pull(Disease) %>%
  unique()

df_plot <- df %>%
  filter(Disease %in% sig_diseases) %>%
  mutate(
    `HR_or_OR[95%CI]` = str_split(`HR_or_OR[95%CI]`, " ") %>% map_chr(1) %>% as.numeric(),
    Disease_category = gsub("Chapter [IVX]+ ", "", Disease_category) %>% str_wrap(width = 25),
    Disease = str_wrap(Disease, width = 40),
    Protein = factor(Protein, levels = unique(c(proteins_1, proteins_2)))
  )

# Create separate plots for each category
categories <- unique(df_plot$Disease_category)

plot_list <- lapply(categories, function(cat) {
  df_cat <- df_plot %>% filter(Disease_category == cat)
  
  ggplot(df_cat, aes(
    x = Protein,
    y = reorder_within(Disease, by = -log2(P_value), within = Disease_category),
    size = -log10(P_value),
    fill = log2(`HR_or_OR[95%CI]`)
  )) +
    geom_point(
      shape = 21,
      color = "black",
      stroke = LINE_WIDTH
    ) +
    turboid_theme() +
    theme(panel.grid.major = element_line(color = "grey90", linewidth = LINE_WIDTH)) +
    scale_fill_gradient2(
      high = "red",
      low = "blue",
      mid = "white",
      limits = c(-2.3, 2.3),
      midpoint = 0,
      na.value = "red"
    ) +
    scale_size_continuous(range = c(0.5, 3.8), breaks = c(20, 40, 60)) +
    theme(
      strip.text = element_text(
        size = FONT_SIZE,
        color = "black",
        family = FONT_FAMILY
      ),
      axis.text.x = element_text(
        size = FONT_SIZE,
        color = "black",
        family = FONT_FAMILY,
        angle = 45,
        vjust = 1,
        hjust = 1
      ),
      legend.spacing.y = unit(5, "mm"),
      legend.position = if(cat == "Chapter I Certain infectious and parasitic diseases") "right" else "none",
    ) +
    labs(
      x = NULL,
      y = NULL,
      fill = expression("log"[2] * "(association)"),
      size = expression("-log"[10] * "(p-value)")
    ) +
    guides(fill = guide_colorbar(
      barwidth = 0.6,
      barheight = 4,
    )) +
    scale_y_reordered() +
    ggtitle(cat)
})

# Combine plots with patchwork in p1 | (p2 / p3) layout
plt <- plot_list[[3]] | (plot_list[[2]] / plot_list[[1]]) +
  plot_layout(guides = "collect") +
  plot_annotation(theme = theme(plot.margin = margin(0, 0, 0, 0))) &
  theme(
    plot.title = element_text(size = FONT_SIZE, family = FONT_FAMILY),
    plot.margin = margin(2, 2, 2, 2)
  )

print(plt)

save_plot <- function(fn, wd, ht) {
ggsave(
  paste0(PLOT_RESULTS_PATH, fn, ".pdf"),
  width = wd,
  height = ht,
  dpi = 300,
  device = cairo_pdf
)
}

save_plot(
fn = "7c_dot_plot_circulatory_endocrine",
wd = 6,
ht = 5.2
)
```


```{r}
# Example with free space
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(~ class, scales = "free_y", space = "free")
```


# 7D
```{r, fig.height=3.8, fig.width=4.2}
plt <- bubble_plot(
  proteins = c("APOA4","SERPINF1","BCHE","LIFR","ITIH3","C7","FGL1","AMBP","GSN","GHR"),
  chapters = c(
    "Chapter I Certain infectious and parasitic diseases",
    "Chapter III Diseases of the blood and blood-forming organs and certain disorders involving the immune mechanism"
  )
)
print(plt)
save_plot(
  fn = "7d_infectious_disease_dot_plot",
  wd = 4.2,
  ht = 3.8
)
```

## 7B: Correlation plot

x is plasma fasting vs basal y is plasma HFD vs chow 6w colors???

```{r, fig.width=4, fig.height=2}
correlation_min <- -4
correlation_max <- 4

correlation_plot(
  timepoints = c(
    "x" = "20221130_EV1_137", # x is adipocyte plasma, fast condition
    "y" = "20240401_CRW_B13" # y is adipocyte plasma, 6w HFD condition
  ),
  sample_type = c(
    "x" = "plasma",
    "y" = "plasma"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "plasma, fasting p < 0.05" = "#85c6ed",
    "plasma, 6w HFD p < 0.05" = "orange",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#B03D00"
  ),
  num_top = 7,
  x_lab = expression("plasma, log"[2] * "(fasting/basal)"),
  y_lab = expression("plasma, log"[2] * "(6w HFD/chow)"),
  drop = "LPS"
)


save_plot(
  fn = "7b_correlation_6w",
  wd = 2,
  ht = 4
)

correlation_plot(
  timepoints = c(
    "x" = "20221130_EV1_137", # x is adipocyte plasma, fast condition
    "y" = "20240917_CRW_B30" # y is adipocyte plasma, 15w HFD condition
  ),
  sample_type = c(
    "x" = "plasma",
    "y" = "plasma"
  ),
  min = correlation_min,
  max = correlation_max,
  correlation_palette = c(
    "plasma, fasting p < 0.05" = "#85c6ed",
    "plasma, 15w HFD p < 0.05" = "orange",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#B03D00"
  ),
  num_top = 7,
  x_lab = expression("plasma, log"[2] * "(fasting/basal)"),
  y_lab = expression("plasma, log"[2] * "(15w HFD/chow)"),
  drop = "LPS"
)


save_plot(
  fn = "7b_correlation_15w",
  wd = 2,
  ht = 4
)
```
# Tissue fast vs HFD iWAT

```{r}
correlation_min <- -7.5
correlation_max <- 4.8

correlation_plot(
  timepoints = c(
    "x" = "20220807_EV1_101", # x is adipocyte tissue, fast condition
    "y" = "20240427_CRW_B17A" # y is adipocyte tissue, 6w HFD condition
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "tissue"
  ),
  min = correlation_min, max = correlation_max,
  correlation_palette = c(
    "tissue, fasting p < 0.05" = "#85c6ed",
    "tissue, 6w HFD p < 0.05" = "orange",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#B03D00"
  ),
  num_top = 7,
  x_lab = expression("tissue, log"[2] * "(fasting/basal)"),
  y_lab = expression("tissue, log"[2] * "(6w HFD/chow)"),
  drop = "LPS"
)


save_plot(
  fn = "7x_tissue_correlation_6w",
  wd = 2,
  ht = 4
)

correlation_plot(
  timepoints = c(
    "x" = "20220807_EV1_101", # x is adipocyte tissue, fast condition
    "y" = "20240907_CRW_B25A" # y is adipocyte tissue, 15w HFD condition
  ),
  sample_type = c(
    "x" = "tissue",
    "y" = "tissue"
  ),
  min = correlation_min,
  max = correlation_max,
  correlation_palette = c(
    "tissue, fasting p < 0.05" = "#85c6ed",
    "tissue, 15w HFD p < 0.05" = "orange",
    "Not significant" = not_significant,
    "Both p < 0.05" = "#B03D00"
  ),
  num_top = 7,
  x_lab = expression("tissue, log"[2] * "(fasting/basal)"),
  y_lab = expression("tissue, log"[2] * "(15w HFD/chow)"),
  drop = "LPS"
)


save_plot(
  fn = "7x_tissue_correlation_15w",
  wd = 2,
  ht = 4
)
```


# ER stress 5C version

```{r, fig.width=2, fig.height=2}

iwat_hfd_6w <- "#f7941d"
ewat_hfd_6w <- "#fede27"
iwat_hfd_15w <- "#ef4136"
ewat_hfd_15w <- "#9f1e37"
both <- "#7E614899"

correlation_plot <-
  function(timepoints,
           sample_type,
           min,
           max,
           correlation_palette,
           num_top = 6,
           x_lab,
           y_lab,
           drop = NULL,
           top = c()) {
    # constants for defining position of margins
    margin_factor <- 0.85
    margin_position <- min * margin_factor
    missing_point_value <- (min + margin_position) / 2

    combined_df <- NULL
    for (timepoint in names(timepoints)) {
      df <-
        read_experiment(timepoints[timepoint], sample_type[timepoint])
      print("df")
      print(colnames(df))
      df <- df %>%
        dplyr::select(
          starts_with("log2_FC"),
          starts_with("-log10_pval"),
          uniprot_id,
          `Entry Name`,
          Symbol_human_jackson_homology_db
        ) %>%
        add_alias() %>%
        mutate(time_point = timepoint) %>%
        dplyr::select(-contains("cre+")) %>%
        dplyr::select(-contains(drop))
      colnames(df) <-
        c(
          "log2_FC",
          "log10_pval",
          "uniprot_id",
          "Entry Name",
          "Symbol_human_jackson_homology_db",
          "protein",
          "alias",
          "time_point"
        )
      combined_df <- rbind(df, combined_df)
    }

    log_threshold <- -log10(0.05)
    
    print("Combined DF")
    print(colnames(combined_df))

    wide_df <- combined_df %>%
      pivot_wider(
        names_from = time_point,
        values_from = c(log2_FC, log10_pval)
      )
    print("Wide DF")
    print(colnames(wide_df))
    #return(wide_df)

    
    combined_df <- wide_df %>%
      mutate(
        significance = case_when(
            (alias %in% er_stress) & ((log10_pval_y > log_threshold) | (log10_pval_x > log_threshold))~ names(correlation_palette[1])[1],
            (alias %in% er_stress) ~ names(correlation_palette[2])[1],
          TRUE ~ names(correlation_palette[3])[1]
        )
      ) %>%
      mutate(
        significance = factor(significance, levels = names(correlation_palette)),
        dist_from_orig = sqrt(log2_FC_x^2 + log2_FC_y^2),
        distance_from_identity = abs(log2_FC_x - log2_FC_y)
      ) %>%
      arrange(desc(significance))

    # calculate pearson's correlation from complete cases
    pearson_r <- cor(combined_df$log2_FC_x, combined_df$log2_FC_y, use = "complete.obs") %>%
      round(digits = 2)


    print(max(combined_df$log2_FC_x, na.rm = TRUE))
    print(max(combined_df$log2_FC_y, na.rm = TRUE))
    print(min(combined_df$log2_FC_x, na.rm = TRUE))
    print(min(combined_df$log2_FC_y, na.rm = TRUE))

    combined_df <- combined_df %>%
      # replace missing values with values on the margins
      replace_na(list(log2_FC_x = missing_point_value, log2_FC_y = missing_point_value))

    # pull list of proteins to give text labels
    significant_no_missing <- combined_df %>%
      filter(
        significance == names(correlation_palette[1])[1],
        log2_FC_x != missing_point_value,
        log2_FC_y != missing_point_value
      )
    label_data <- rbind(
      # top by distance from identity
      significant_no_missing %>%
        arrange(distance_from_identity) %>%
        tail(num_top),
      # top by distance from origin
      significant_no_missing %>%
        arrange(dist_from_orig) %>%
        tail(num_top),
      # top only quantified at x
      combined_df %>%
        arrange(abs(log2_FC_x)) %>%
        filter(
          significance == names(correlation_palette[1])[1],
          (log2_FC_y == missing_point_value)
        ) %>%
        tail(num_top / 2),
      # top only quantified at y
      combined_df %>%
        arrange(abs(log2_FC_y)) %>%
        filter(
          significance == names(correlation_palette[1])[1],
          (log2_FC_x == missing_point_value)
        ) %>%
        tail(num_top / 2)
    ) %>% distinct()
    
    if (length(top) > 0){
      label_data <- combined_df %>% filter(alias %in% top)
    }
    
    combined_df %>% 
      filter(significance == names(correlation_palette[1])[1] ) %>%
      pull(log2_FC_x) %>%
      abs() %>%
      max() %>%
      print()
    
      combined_df %>% 
      filter(significance == names(correlation_palette[1])[1] ) %>%
      pull(log2_FC_y) %>%
      abs() %>%
      max() %>%
      print()

    plot <- combined_df %>%
      ggplot(aes(
        x = log2_FC_x,
        y = log2_FC_y,
        fill = significance,
        label = alias
      )) +
      # margin lines
      geom_hline(
        yintercept = margin_position,
        size = LINE_WIDTH,
        color = "black"
      ) +
      geom_vline(
        xintercept = margin_position,
        size = LINE_WIDTH,
        color = "black"
      ) +
      # origin lines
      geom_hline(
        yintercept = 0,
        color = "grey90",
        size = LINE_WIDTH
      ) +
      geom_vline(
        xintercept = 0,
        color = "grey90",
        size = LINE_WIDTH
      ) +
      # diagonal boundary lines
      geom_segment(
        data = data.frame(),
        aes(
          x = c(margin_position, margin_position, margin_position + 1),
          y = c(margin_position + 1, margin_position, margin_position),
          xend = c(max - 1, max, max),
          yend = c(max, max, max - 1),
          linetype = c("dashed", "solid", "dashed")
        ),
        size = LINE_WIDTH,
        inherit.aes = FALSE,
        show.legend = FALSE,
        color = "black"
      ) +
      # scatterplot
      geom_point(
        shape = 21,
        stroke = 0,
        alpha = 0.55,
        size = 1.4,
      ) +
      # protein labels
      geom_text_repel(
        data = label_data,
        size = 1.94028,
        family = FONT_FAMILY,
        min.segment.length = 0,
        #force = 3,
        segment.size = LINE_WIDTH,
        max.overlaps = Inf,
        #nudge_y = -2,
        #nudge_x = 2,
        show.legend = FALSE#,
        #segment.curvature = -0.1,
      #segment.ncp = 3,
      #segment.angle = 45
      ) +
      turboid_theme() +
      theme(
        aspect.ratio = 1,
        # 20 lines of legend formatting
        legend.position = "top",
        legend.text = element_text(
          size = 6,
          color = "black",
          family = "Arial",
          margin = margin(l = 0)
        ),
        legend.box.background = element_blank(),
        legend.justification.top = "top",
        legend.justification = "center",
        legend.box.just = "center",
        legend.key = element_blank(),
        legend.margin = margin(l = -5, b = -5.5),
        legend.box.margin = margin(l = -5, b = -0.8),
        legend.key.spacing.y = unit(-0.9, "cm"),
        legend.key.spacing.x = unit(-0.1, "cm")
      ) +
      guides(fill = guide_legend(nrow = 2, override.aes = list(alpha = 1))) +
      labs(
        x = x_lab,
        y = y_lab
      ) +
      scale_fill_manual(values = correlation_palette, name = NULL) +
      scale_x_continuous(expand = expansion(mult = 0), limits = c(min, max)) +
      scale_y_continuous(expand = expansion(mult = 0), limits = c(min, max)) +
      scale_linetype_manual(values = c("dashed" = "dashed", "solid" = "solid")) +
      geom_text(
        mapping = aes(
          x = min * 0.6,
          y = max * 0.85,
        ),
        label = paste("R = ", as.character(pearson_r)),
        inherit.aes = FALSE,
        data = data.frame(),
        size = 1.94028,
        family = FONT_FAMILY
      )

    return(combined_df)
  }

combined_df <- correlation_plot(
  timepoints = c(
    "x" = "20240907_CRW_B25A",
    "y" = "20240909_CRW_B25B"
  ),
  min = -8,
  max = 5.5,
  sample_type = c("x" = "tissue", "y" = "tissue"),
  num_top = 7,
  correlation_palette = c(
    "ER stress, significant p < 0.05" = "plum4",
    "ER stress, non-significant p > 0.05" = "pink3",
    "Other" = "grey90"
  ),
  drop = "blank",
  x_lab = expression("iWAT 15w, log"[2] * "(HFD/chow)"),
  y_lab = expression("eWAT 15w, log"[2] * "(HFD/chow)")
)
save_plot("5x_er_stress_correlation_plot",
  wd = 2,
  ht = 4
)

```


```{r}
combined_df %>%
  filter(significance == "ER stress, significant p < 0.05") %>%
  arrange(abs(log2_FC_y))

# x = 1.75
# y =1.7
```



## 7b Dot plot

```{r, fig.height=2.5, fig.width=4.75}
fold_change_dot_plot <- function(highlight_genes, drop_groups = c()) {
  df <- dep_path %>% 
    read_csv(show_col_types = FALSE) %>%
    filter(
      comparison %in% c(
        "LPS vs. basal",
        "fast vs. basal",
        "HFD vs. chow",
        "eWAT_HFD vs. eWAT_chow",
        "iWAT_HFD vs. iWAT_chow"
      )
    ) %>%
    mutate(
      time_point = replace_na(time_point, ""),
      comparison = paste(time_point, comparison)
    )
  df <- df %>%
    mutate(`Entry Name` = entry_name) %>%
    add_alias() %>%
    filter(
      experiment %in% c(
        # fast / LPS in tissue
        "20220714_EV1_98",
        "20220807_EV1_101",
        # fast / LPS in plasma
        "20221129_EV1_136",
        "20221130_EV1_137",
        # chow / HFD in plasma,
        "20240401_CRW_B13",
        "20240917_CRW_B30",
        # chow / HFD in tissue 15w
        "20240909_CRW_B25B",
        "20240907_CRW_B25A",
        # chow / HFD in tissue 6w
        "20240427_CRW_B17A",
        "20240429_CRW_B17B"
      )
    ) %>%
    mutate(
      tissue = case_when(
        grepl("EV1_136|EV1_98", experiment) ~ "Hepatocyte",
        grepl("EV1_101|B17A|B25A", experiment) ~ "Adipocyte iWAT",
        grepl("B17B|B25B", experiment) ~ "Adipocyte eWAT",
        grepl("B13|B30|EV1_137", experiment) ~ "Adipocyte",
        grepl("eWAT", comparison) ~ "Adipocyte eWAT",
        grepl("iWAT", comparison) ~ "Adipocyte iWAT",
        TRUE ~ comparison
      )
    ) %>%
    filter(alias %in% highlight_genes) %>%
    mutate(
      comparison = str_split(comparison, " vs. ") %>% map_chr(1),
      comparison = gsub("eWAT_|iWAT_", "", comparison),
      comparison = trimws(comparison),
      comparison = recode(comparison, !!!c("fast" = "fasting")),
      alias = factor(alias, levels = rev(highlight_genes)),
      group = paste0(tissue, "\n", sample_type),
      group = gsub(pattern = " iWAT\ntissue", replacement = "\niWAT tissue", x = group),
      group = gsub(pattern = " eWAT\ntissue", replacement = "\neWAT tissue", x = group),
      group = gsub(pattern = "serum", replacement = "plasma", x = group),
      group = factor(
        group,
        levels = c(
          "Adipocyte\niWAT tissue",
          "Adipocyte\neWAT tissue",
          "Adipocyte\nplasma",
          "Hepatocyte\ntissue",
          "Hepatocyte\nplasma"
        )
      ),
      comparison = factor(comparison, levels = c("fasting", "LPS", "6w HFD", "15w HFD"))
    ) %>%
    filter(!(group %in% drop_groups))
  
    cluster_df <- df %>%
    select(alias, comparison, group, log2_FC) %>%
    unite("condition", comparison, group, sep = "_") %>%
    distinct(alias, condition, .keep_all = TRUE) %>%
    pivot_wider(names_from = condition, values_from = log2_FC) %>%
    column_to_rownames("alias")
    
     priority_proteins <- c("SYUG", "LEP")
  cluster_proteins <- setdiff(rownames(cluster_df), priority_proteins)
  cluster_matrix <- as.matrix(cluster_df[cluster_proteins, ])
  
  
  hc <- hclust(dist(cluster_matrix, method = "euclidean"), method = "complete")
  clustered_order <- rownames(cluster_matrix)[hc$order]
  
  final_order <- c(clustered_order, priority_proteins)
  
  df <- df %>%
    mutate(alias = factor(alias, levels = final_order))
  
  
  plt <- df %>% ggplot(aes(
    x = comparison,
    y = alias,
    fill = log2_FC,
    size = `-log10_pval`
  )) +
    geom_point(shape = 21, stroke = LINE_WIDTH) +
    facet_grid(
      cols = vars(group),
      scales = "free_x",
      space = "free"
    ) +
    turboid_theme() +
    theme(
      panel.spacing.x = unit(0, "mm"),
      panel.grid.major = element_line(color = "grey", linewidth = LINE_WIDTH),
      strip.placement = "outside",
      strip.text = element_text(family = FONT_FAMILY, size = FONT_SIZE, color = "black", margin = margin(b = 2)),
      legend.position = "bottom",
      strip.position = "bottom",
      legend.key.height = unit(3, "mm"),
      legend.key.width = unit(4, "mm")
    ) +
    scale_fill_gradient2(
      high = "red",
      low = "blue",
      mid = "white",
      limits = c(-3, 3),
      oob = squish,
      name = expression("log"[2] * "(FC from basal or chow)")
    ) +
    scale_size_continuous(
      range = c(1, 3.8),
      name = expression("-log"[10] * "(p-value)")
    ) +
    labs(x = NULL, y = NULL)
  print(plt)
  return(plt)
}

proteins_7b <- c("LEP","SYUG","CFD","LRG1","APOA4","PAM","SERPINF1","BCHE","LIFR","ITIH3","FGL1","C7","AMBP","GSN","GHR")
fold_change_dot_plot(
  highlight_genes = proteins_7b
) + theme(axis.text.x = element_text(family = FONT_FAMILY, size = FONT_SIZE, color = "black", angle = 45, hjust = 1, vjust = 1))
save_plot("7b_fc_dot_plot", ht = 2.5, wd = 4.75)
```

```{r, fig.width=2, fig.height=1.5}
fold_change_dot_plot(
  highlight_genes =
    c(
      "CDNF",
      "MANF",
      "NENF"
    ), drop_groups = c("Hepatocyte\ntissue", "Adipocyte\nserum")
) + theme(axis.text.x = element_text(family = FONT_FAMILY, size = FONT_SIZE, color = "black", angle = 45, hjust = 1, vjust = 1))

save_plot("s5A_dot_plot", 2, 1.5)
```

```{r, fig.width=4.75, fig.height=2.7}
fold_change_dot_plot(
  highlight_genes =
    c('B2MG',
 'C1RA',
 'C7',
 'C8B',
 'CFD',
 'ERAP1',
 'FBLN3',
 'FCN1',
 'G6PE',
 'GHR',
 'LBP',
 'PCYOX',
 'SERPINA3N',
 'SERPINF1',
 'TRFE'), 
) + theme(axis.text.x = element_text(family = FONT_FAMILY, size = FONT_SIZE, color = "black", angle = 45, hjust = 1, vjust = 1))

save_plot("s6g_fc_dot_plot", 4.75, 2.7)
```




```{r, fig.height=5.8, fig.width=2.8}
fold_change_dot_plot <- function(highlight_genes) {
  df <- dep_path %>%
    read_csv(show_col_types = FALSE) %>%
    filter(
      comparison %in% c(
        "LPS vs. basal",
        "fast vs. basal",
        "HFD vs. chow",
        "eWAT_HFD vs. eWAT_chow",
        "iWAT_HFD vs. iWAT_chow",
        "eWAT_HFD vs. iWAT_HFD",
        "eWAT_chow vs. iWAT_chow"
      )
    ) %>%
    mutate(
      time_point = replace_na(time_point, ""),
      comparison = paste(time_point, comparison)
    )

  df <- df %>%
    mutate(`Entry Name` = entry_name) %>%
    add_alias() %>%
    filter(
      experiment %in% c(
        # fast / LPS in tissue
        # "20220714_EV1_98",
        "20220807_EV1_101",
        # fast / LPS in plasma
        # "20221129_EV1_136",
        "20221130_EV1_137",
        # chow / HFD in plasma,
        "20240401_CRW_B13",
        "20240917_CRW_B30",
        # chow / HFD in tissue 15w
        "20240909_CRW_B25B",
        "20240907_CRW_B25A",
        # chow / HFD in tissue 6w
        "20240427_CRW_B17A",
        "20240429_CRW_B17B",
        # iWAT vs eWAT
        "20240430_CRW_B17C",
        "20240501_CRW_B17D",
        "20240911_CRW_B25C",
        "20240915_CRW_B25D"
      )
    ) %>%
    mutate(
      tissue = case_when(
        grepl("EV1_136|EV1_98", experiment) ~ "Hepatocyte",
        grepl("EV1_101|B17A|B25A", experiment) ~ "Adipocyte\n(iWAT)",
        grepl("B17B|B25B", experiment) ~ "Adipocyte\n(eWAT)",
        grepl("B13|B30|EV1_137", experiment) ~ "Adipocyte",
        # grepl("eWAT", comparison) ~ "Adipocyte (eWAT)",
        # grepl("iWAT", comparison) ~ "Adipocyte (iWAT)",
        TRUE ~ "Adipocyte"
      )
    ) %>%
    filter(alias %in% highlight_genes) %>%
    mutate(
      comparison = str_split(comparison, " vs. ") %>% map_chr(1),
      comparison = case_when(
        tissue == "Adipocyte" ~ gsub("eWAT_", "eWAT/iWAT ", comparison),
        TRUE ~ gsub("eWAT_", "", comparison)
      ),
      comparison = gsub("iWAT_", "", comparison),
      comparison = trimws(comparison),
      comparison = recode(comparison, !!!c("fast" = "fasting")),
      # alias = factor(alias, levels = rev(highlight_genes)),
      alias = as.character(alias), alias = case_when(grepl(pattern = "GO:0005783", x = `Gene Ontology (GO)`) ~ paste0("*", alias), TRUE ~ alias),
      group = paste0(tissue, "\n", sample_type),
      group = factor(
        group,
        levels = c(
          "Adipocyte\n(iWAT)\ntissue",
          "Adipocyte\n(eWAT)\ntissue",
          "Adipocyte\ntissue",
          "Hepatocyte\ntissue",
          "Adipocyte\nserum",
          "Hepatocyte\nserum"
        )
      ) # ,
      # comparison = factor(comparison, levels = c("fasting", "LPS", "6w HFD", "15w HFD", "eWAT"))
    )
  sig_aliases <- df %>%
    filter(Regulation %in% c("Significant Down", "Signficant Up")) %>%
    pull(alias) %>%
    as.character() # Convert factor to character
  df <- df %>% filter(as.character(alias) %in% sig_aliases)
  # try to sort proteins by first column
  sort_order <- df %>%
    filter(tissue == as.character("Adipocyte\n(iWAT)"), comparison == "15w HFD") %>%
    arrange(log2_FC) %>%
    pull(alias) %>%
    as.character()

  # Get all unique proteins in the dataset
  all_proteins <- unique(as.character(df$alias))

  # Combine: sorted proteins first, then any remaining proteins
  a_levels <- c(setdiff(all_proteins, sort_order), sort_order)

  df <- df %>%
    mutate(alias = as.character(alias), alias = factor(alias, levels = a_levels)) %>%
    arrange(alias)

  plt <- df %>% ggplot(aes(
    x = comparison,
    y = alias,
    fill = log2_FC,
    size = `-log10_pval`
  )) +
    geom_point(shape = 21, stroke = LINE_WIDTH) +
    facet_grid(
      cols = vars(group),
      scales = "free_x",
      space = "free"
    ) +
    turboid_theme() +
    theme(
      panel.spacing.x = unit(0, "mm"),
      panel.grid.major = element_line(color = "grey", linewidth = LINE_WIDTH),
      strip.placement = "outside",
      strip.text = element_text(family = FONT_FAMILY, size = FONT_SIZE, color = "black", margin = margin(b = 2)),
      legend.position = "bottom",
      axis.text.x = element_text(
        size = FONT_SIZE,
        color = "black",
        family = FONT_FAMILY,
        angle = 45,
        vjust = 1,
        hjust = 1
      ),
      legend.key.height = unit(3, "mm"),
      legend.key.width = unit(4, "mm"),
      legend.box.spacing = unit(0.5, "cm"),
      legend.box.margin = margin(l = 0, b = 0)
    ) +
    scale_fill_gradient2(
      high = "red",
      low = "blue",
      mid = "white",
      limits = c(-3, 3),
      oob = squish,
      name = expression("log"[2] * "(FC)")
    ) +
    scale_size_continuous(
      range = c(1, 3),
      name = expression("-log"[10] * "(p-value)")
    ) +
    labs(x = NULL, y = NULL)
  print(plt)
  save_plot("depot_proteins", ht = 5.8, wd = 2.8)
  return(df)
}
er_stress <- c("A0A1B0GS74", "A2AIX1", "MA1B1", "A2AJP5", "SELN", "PDIA2", "E9PW77", "UBE4A", "ATF6A", "G3UYF5", "G3X8R5", "FBX50", "J3QM81", "BAK", "CASPC", "P85B", "FLOT1", "M3K5", "BOK", "XBP1", "RNF5", "ATF6B", "CSN5", "B2L11", "NCK2", "AGR2", "STC2", "NEMO", "APAF", "ABL1", "INS2", "IFNG", "JUN", "PDIA4", "ENPL", "PDIA1", "BCL2", "ITPR1", "A4", "CALR", "DDX3L", "PMP22", "PR15A", "GRP78", "CCND1", "CFTR", "P85A", "MARCS", "RGRF1", "PDIA3", "CEBPB", "AKT1", "CALX", "DDIT3", "PTN1", "MA1A2", "LOX15", "LOX5", "CAV1", "CLGN", "PDX1", "FAF1", "WFS1", "UBP25", "ERP29", "SESN2", "OPA1", "UB2G2", "NPL4", "UBE2K", "TM258", "UFM1", "PRS10", "PP2AB", "AUP1", "UFD1", "BID", "CASP3", "KCNJ8", "PLPL9", "TERA", "E2AK2", "PTN2", "ATF4", "CLUS", "BAX", "EDEM3", "FAF2", "STT3B", "Q3TML0", "MANF", "Q3TQS0", "Q3TTF2", "PARP8", "RNFT2", "DAB2P", "UBP19", "FXRD2", "ERMP1", "NIBAN", "SVIP", "SE1L2", "TMUB2", "Q3V3N7", "UBP13", "LRRK2", "RN145", "JAGN1", "NR1H2", "ATF3", "NF2L2", "AKT2", "PML", "BAP31", "TRI25", "ELAV4", "NF2L1", "DDX3X", "B2CL1", "AT2A3", "BRSK2", "CE290", "FBX27", "Q6NXK9", "IF4G1", "UB2J2", "PARP6", "ECM29", "SERP2", "MARH6", "SPOP", "IF2A", "PAR16", "RN139", "FBX2", "DDRGK", "Q80YQ1", "PR15B", "ERLN2", "TMTC4", "UBX10", "TM117", "CR3L2", "Q8BH80", "RCN3", "NOD1", "RHBL4", "AQP11", "JKAMP", "FICD", "EDEM2", "SGTA", "EIF2A", "NRROS", "DERL2", "NHLC1", "TMTC3", "CASP9", "OTU1", "UFL1", "CRERF", "EI2BE", "MBTP2", "MBRL", "DNM1L", "OS9", "TM129", "ANS4B", "NOD2", "TRIB3", "RN183", "BFAR", "ERO1A", "UBAC2", "ATG10", "RN121", "UBQL1", "CHAC1", "AT2A1", "TMX1", "RPAP2", "UBXN4", "NRBF2", "UBA5", "ERLEC", "MBOA5", "ABCA7", "UROM", "ERLN1", "CR3L3", "RN185", "DNJC3", "TADBP", "TMCO1", "UBXN1", "SIR1", "EDEM1", "DERL1", "GORS2", "UBX2A", "CK5P3", "PARK7", "NCK1", "BBC3", "UBXN6", "SELS", "ASB11", "FIS1", "SC61B", "TXD12", "UFC1", "TMM33", "ATX3", "TRI13", "Q9CZ70", "CCD47", "GET4", "ERP44", "RN186", "BI1", "DERL3", "ERP27", "CALR3", "SGF29", "LFG4", "BBS10", "SYVN1", "DJC10", "IRGM3", "RNFT1", "C43BP", "ERN1", "TOR1A", "UBE4B", "AFF4", "LFG1", "MLTK", "SDF2L", "HERP2", "HERP1", "UB2J1", "SCAM5", "HYOU1", "SELK", "APR", "UBP14", "TMUB1", "BHA15", "DJB12", "DNJB2", "DNJB9", "E2AK4", "SERC3", "UBQL2", "TR10B", "FBX17", "FBX6", "AMFR", "TBL2", "SRPX", "TMED2", "RN103", "NUPR1", "AKT3", "CHIP", "GSK3B", "PRKN2", "AIFM1", "NR1H3", "CR3L1", "BAG6", "TSP4", "SERP1", "E2AK3", "ERN2", "SE1L1")
df <- fold_change_dot_plot(
  highlight_genes = calcium_homeostasis
)


```


